---
title: "EXNAT – Analysis of Lab & Online Data"
author: "Merle Schuckart & Sandra Martin"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r file setup, echo = FALSE}
rm(list = ls()) # clear environment
knitr::opts_chunk$set() # set default options for all code blocks in this document
options(scipen = 999) # don't use scientific notation for very large or small numbers

```

## Load packages
```{r packages, echo = FALSE, message = FALSE, warning = TRUE}

# Create a list with needed libraries
pkgs <- c("here", # for working with relative paths
          "ggeffects", # create data frames of marginal effects for 'ggplot' from model outputs
          "rstudioapi", # for getting path of this file
          "stringr", # for getting substrings
          "ggplot2", # for plots
          "cowplot", # also for plots
          "scales", # for setting pretty axis breaks
          "MKdescr", # for log-axes in ggplot
          "dplyr", # for replacing multiple values in vector with different values
          "reshape2", # for reshaping df format
          "data.table", # for data tables
          "tidyverse", # for aggregating
          "R.utils", # for deleting all empty csv files in the directory
          "psycho", # for computing d-prime values
          "yarrr", # for plotting
          "devtools", # for getting packages from github
          "lattice", # for quick & dirty density plots
          "gtools", # for getting tuples from list
          #"DescTools", # for checking normality of distribution in QQ plot
          "easystats", # also for working with lme4 model output, contains "performance" & "see" I think?
          "see", # for plotting residuals of lme4 model
          "performance", # needed for plotting the lme4 model output summary
          "lme4", # also for linear mixed models, but no p-values in the summary
          "lmerTest", # extension of lme4 - for tab_model() for showing lme4 model results
          "modelsummary", # for printing model fit measures
          "car", # for basic Anova() function & aGSIFs (= basically weird adjusted VIFs)
          "sjPlot", # for running Anova & showing results in a HTML table in the Viewer
          "purrr", # for satterthwaite p-value correction in tab_model function
          "BayesFactor", # that's self-explanatory
          "interactions", # for simple slopes analysis
          "patchwork", # needed for check_model plotting function
          "glmnet", # for elastic net regression
          "caret", # for choosing the best tuning parameters for elastic net regression
          #"beepr", # to play Super Mario sound when script finished running
          "effects", # for plotting lmm interaction & main effects
          "gridExtra", # for showing several plots in a grid
          "mgcv", # for GAMs
          "gratia", # for plotting and assessing GAMs
          "itsadug") # for plotting and assessing GAMs

# Load each listed library, check if it's already installed
# and install if necessary
for (pkg in pkgs){
  if(!require(pkg, character.only = TRUE)){
    install.packages(pkg)
    library(pkg, character.only = TRUE)
  }
}

# install package with lists of stop words from github
devtools::install_github("quanteda/stopwords")
library(stopwords)

```

## Load d-prime function from different R script:
```{r source d-prime function, echo = FALSE}
source(here::here("Analysis/get_dprime.R")) # get script
```


``` {r load word freqs & entropies & surprisal scores for each word}

# load word frequencies
word_freqs_df = read.csv(here::here("Analysis/word frequencies/Word_freqs.csv"), sep = ";", header = TRUE)[2:4]
# Explanation: We compute the word frequencies using another
#              script which is called "calculate_word_frequencies.py".
#              You can find it in the "Analysis/word frequuencies/" folder.
#              --> word frequencies were taken from this python package:
#              Speer, R., Chin, J., Lin, A., Jewett, S., & Nathan, L. (2018, October 3).
#              LuminosoInsight/wordfreq: v2.2. Zenodo. https://doi.org/10.5281/zenodo.1443582


# Load surprisal scores & word entropies
surprisal_df = read.csv(here::here("Analysis/surprisal scores/vanilla_2words_surprisal_entropy.csv"), sep = ",", header = TRUE)
# Explanation: I computed the scores in Python using a German GPT-2 model. For each text you can select a context chunk of 2 words
#              and predict the next word. For each possible continuation of your context, you get probabilities.
#              If you get the probability for the actual word and compute the negative log of it, you have the surprisal score
#              for your word. 
#              The entropies however reflect the distribution of the probabilities. If the model is very "confident" about 
#              a certain next word prediction, the entropy will be low, if a lot of continuations seem possible, the entropy will be higher.
#              The script for generating surprisal scores and entropies is located here: 
#              "Analysis/surprisal scores/Surprisal Scores Generation/Surprisal_Vanilla.py"

```


## Load df from RData
```{r}
# df cleaned from outliers and without n-back tasks
# load(here::here("Analysis/RData/df_clean_all_subjects.RData")) - old
load(here::here("Analysis/RData/df_clean_all_subjects_09_24.RData"))

# df for lmm: without outliers and without n-back tasks
# load(here::here("Analysis/RData/lmm_df_all_subjects.RData")) 
load(here::here("Analysis/RData/lmm_df_all_subjects_09_24.RData")) 

# df with comprehension question performance:
#load(here::here("Analysis/RData/df_comprehension_Qs.RData")) 

# load demographics df:
#load(here::here("Analysis/RData/df_demogr.RData")) 


# load lmm results:
# m_dprimes <- readRDS(here::here("Analysis/RData/m_dprimes.rds"))
# m_compr_Qs <- readRDS(here::here("Analysis/RData/m_compr_Qs.rds"))
m_RT_ts2_age_centered_random_slope_entropy <- readRDS(here::here("Analysis/RData/Mixed_models/m_RT_ts2_age_centered_random_slope_entropy.rds"))
m_RT_ts2_No_centering_age_random_slope_entropy <- readRDS(here::here("Analysis/RData/Mixed_models/m_RT_ts2_No_centering_age_random_slope_entropy.rds"))

m_RT_ts2_age_centered_online_sample <- readRDS(here::here("Analysis/RData/Mixed_models/m_RT_ts2_age_centered_online_sample.rds"))
m_RT_ts2_age_centered_replication_sample <- readRDS(here::here("Analysis/RData/Mixed_models/m_RT_ts2_age_centered_replication_sample.rds"))

# load gam result
m_gam_RT_ts2 <- readRDS(here::here("Analysis/RData/Mixed_models/m_gam_RT_ts2.rds"))

# load model comparison of lmm and gam (calculation takes over an hour)
model_comp_lmm_gam <- readRDS(here::here("Analysis/RData/Mixed_models/model_comp_lmm_gam.rds"))

# load simple slopes results
load(here::here("Analysis/RData/Mixed_models/simslopes_ts2_240925.RData")) # simple slopes for lmm ts2

# ------------------

# Load preprocessed replication data:
  
load(here::here("Analysis/RData/replication_lmm_df.RData"))
load(here::here("Analysis/RData/replication_df_comprehension_Qs.RData"))
load(here::here("Analysis/RData/replication_df_demogr.RData"))


```


## Settings for plots
```{r Theme for plots, echo = FALSE}
apatheme <- theme_bw()+
  theme(plot.title = element_blank(), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line = element_line(),
        text = element_text(family = 'sans',size = 14)) #panel.grid.major=element_blank(),

today <- Sys.Date()
today <- format(today, format="%y%m%d")


# Custom colour palettes for the plots:

# for distinguishing between age groups:
palet_lab_online <- c("#D2BFE7", # lab
                      "#977FB2") # online

# for distinguishing between cognitive load conditions: 
palet_load <- c("#575A7B", # Reading Only
                "#ED9201", # 1-back
                "#982126") # 2-back
# --> I used these on my poster for the different n-back conditions, 
#     should be distinguishable even for people with impaired colour vision - Merle

# for distinguishing between n-back tasks (single- & dual 1- and 2-back)
palet_dprimes = c("#ED9201", # 1-back Dual
                  "#fec160", # 1-back Single
                  "#982126", # 2-back Dual
                  "#d95459") # 2-back Single
palet_dprimes_lines = c("#cb7d00", # 1-back Dual
                        "#ED9201", # 1-back Single
                        "#982126", # 2-back Dual
                        "#d95459") # 2-back Single

# for simple slopes plots:
palet_simple_slopes = c("#585858", # n.s.
                        "#0c6ae8") # sign.

# For effects we don't really have colours for. Like age or surprisal.
palet_effects <- c("#365464") 

```


## Set path to datasets
```{r path setup, echo = FALSE}
# online and lab data should be all in 1 folder:
path_data_folder <- here::here("Analysis/Data/raw_data/")
```



## Read in data & do preprocessing on participant-level

In this chunk, we read in every dataset individually, compute reading times, reading speed, d-primes, comprehension question performance, and so on, 
add a few information on the words we used (e.g. surprisal scores on our 4 time scales, word frequencies, word lengths, punctuation,...), 
and then we exclude data on participant- and block-level:
We only exclude participants if they were distracted during the experiment or we noticed recording errors.
We only exclude data on block-level if performance measures indicate they didn't do the task(s) correctly.

```{r read in and preprocess data, echo = FALSE}

# Get list of all .csv files in the data folder
# --> online data from Lübeck & lab data from Leipzig are all in one folder
# --> The online datasets have a long string of numbers and letters as a name, 
#     the lab datasets are called YA + a number for the younger adults and OA + a number for the older adults.
file_list <- list.files(path = path_data_folder, pattern='.csv')

# Placeholders df for demographics, questions & text data
df_demogr           <- data.frame()
df_text_data        <- data.frame()
df_comprehension_Qs <- data.frame()

# Loop files in my file list aka directory
for (i in 1:length(file_list)) {

  # PREPARE FILE FOR PREPROCESSING
  # Read in current file
  subj_df <- read.csv(paste(path_data_folder, file_list[i],sep = ""), sep = ",")

  # If the df is separated by a semicolon instead of a comma, we only get
  # one messed-up column. In this case, use semicolon as separator for csv:
  if (ncol(subj_df) == 1) {
    subj_df <- read.csv(paste(path_data_folder, file_list[i],sep = ""), sep = ";")
  }
  
  # check if we have enough data for the analysis
  # I only want full datasets, but it's not crucial that we have
  # data for the experiment check and the end slide
  # If the session was aborted before,
  # end current iteration & go to next file
  if (length(which(subj_df$sender == "Demographics_2")) < 1){
    message("Participant aborted session prematurely - going to next dataset now")
    next
  }

  ###########################
  
  # Quick plastic surgery for some of the datasets:
  
  # In some datasets, where text 05 is shown in one of the 2-back main blocks, 
  # there are no values for text_nr and block_kind.
  # So add "text_05" and "2back_main" there if the 
  # current dataset has these missing values.
  
  # Check if there is a dataset where comprehension questions for text_05 were shown (= ended on form submission)
  # and there are no values for block_kind and text_nr. If there is one, find the correct row and add the missing data there.
  if (length(subset(subj_df, sender == "Qs text_05" & block_kind == "" & text_nr == "" & ended_on == "form submission")$ID) == 1){
    #print("FIXING SCRIPT DATA SAVING ERROR IN THIS DATASET!")
    subj_df[which(subj_df$sender == "Qs text_05" & subj_df$ended_on == "form submission"),]$block_kind = "2back_main"
    subj_df[which(subj_df$sender == "Qs text_05" & subj_df$ended_on == "form submission"),]$text_nr = "text_05"
    
  }

  # That's it!

  ###########################

  # ADD DEMOGRAPHICS

  # find out in which row the demographic informations are:
  row_demogr1    <- which(subj_df$sender == "Demographics_1")
  row_handedness <- which(subj_df$sender == "Handedness")
  row_ids        <- which(subj_df$sender == "ID")
  row_demogr2    <- which(subj_df$sender == "Demographics_2")

  # get demographical data:
  id                          <- subj_df[row_ids, ]$ID # individual code
  
  age                         <- subj_df[row_demogr1, ]$age # age in years
  gender                      <- subj_df[row_demogr1, ]$gender # gender in passport
  education                   <- subj_df[row_demogr1, ]$education # highest degree
  handedness                  <- subj_df[row_handedness, ]$handedness # handedness

  native_speaker              <- as.logical(subj_df[row_demogr1, ]$native_speaker) # German = mothertongue?
  seeing_impaired             <- as.logical(subj_df[row_demogr1, ]$seeing_impaired) # impaired eyesight?
  seeing_impairment_corrected <- as.logical(subj_df[row_demogr1, ]$glasses_contacts) # currently wearing glasses / contacts?

  # One participant skipped the demographics for some reason, so add the missing information we could reconstruct:
  if (id == "C13RDO"){
    age    <- 31 # age in years
    gender <- "m" # gender in passport
    education <- "undergrad" # highest degree
  } 
  
  
  # add current index to ID so we can distinguish between 
  # participants who happen to have the same ID ("YA005" and "MA007" share an ID unfortunately):
  id <- paste(id, i, sep = "")
  
  # Some datasets were recorded in the lab, some online. 
  # The file names of the ones from the lab start with "YA" for "young adult", and "OA" for "old adult",
  # so save location based on file name.
  
  # If the current file name starts with YA, MA or OA, it's from the lab:
  if (substr(file_list[i], start = 1, stop = 2) == "YA" | 
      substr(file_list[i], start = 1, stop = 2) == "OA" | 
      substr(file_list[i], start = 1, stop = 2) == "MA"){
    recording_location <- "lab"
    
    # information from Prolific (all empty because this only applies to online studies):
    code               <- ""
    confirmation_code  <- ""
    prolific_id        <- ""
    
    # exclusion criteria check --> All FALSE because screened before invitation to the lab
    drugs                       <- FALSE
    alcohol                     <- FALSE
    psych_dis                   <- FALSE
    neur_dis                    <- FALSE
    stroke                      <- FALSE
    medicine                    <- FALSE
    infect_dis                  <- FALSE
    
    # Were all stimuli displayed properly? --> TRUE because lab study
    exp_words_displayed         <- TRUE
    exp_colours_distinguishable <- TRUE
    # any technical issues or distractions? --> FALSE because lab study
    exp_distracted              <- FALSE
    exp_tech_issues             <- FALSE
    row_exp_check <- ""
    
    
  # If the current file doesn't start with YA, MA or OA, it's an online dataset:
  } else {
    recording_location <- "online"
    prolific_id        <- subj_df[row_ids, ]$prolific_ID  # Prolific ID
    
    # Prolific confirmation code for completed experiments
    # and automatically generated participant code:
    code               <- subj_df[1, ]$code
    confirmation_code  <- subj_df[1, ]$confirmationCodeOngoing  
    
    # exclusion criteria check:
    drugs                       <- as.logical(subj_df[row_demogr2, ]$drugs) # took drugs in the past 4 weeks / before / during the experiment?
    alcohol                     <- as.logical(subj_df[row_demogr2, ]$alcohol) # drank alcohol before/during experiment?
    psych_dis                   <- as.logical(subj_df[row_demogr2, ]$psych_disorder) # psychological disorder (e.g. depression)?
    neur_dis                    <- as.logical(subj_df[row_demogr2, ]$neur_disorder) # neurological disease (e.g. dementia)?
    stroke                      <- as.logical(subj_df[row_demogr2, ]$stroke) # has had a stroke in the past?
    medicine                    <- as.logical(subj_df[row_demogr2, ]$medicine) # takes medicine that makes you sleepy?
    infect_dis                  <- as.logical(subj_df[row_demogr2, ]$currently_sick) # feels sick (Covid, Long Covid, cold, RSV,...)
    
    # get information concerning the study (if they made it to the last slide and answered the questions):
    if (length(which(subj_df$sender  == "Experiment_Check"))     > 0){
      # get row where we can find all information concerning the experiment
      row_exp_check               <- which(subj_df$sender == "Experiment_Check")
      # get information
      exp_words_displayed         <- as.logical(subj_df[row_exp_check, ]$exp_check_words_displayed) # could see the words?
      exp_colours_distinguishable <- as.logical(subj_df[row_exp_check, ]$exp_check_colours_distinguishable) # could distinguish the colours easily?
      exp_distracted              <- as.logical(subj_df[row_exp_check, ]$exp_check_distracted) # was distracted (e.g. by a person, music, a movie)?
      exp_tech_issues             <- subj_df[row_exp_check, ]$exp_check_technical_issues # were there technical issues (e.g. internet connection crashing)?
      
    # if the study was ended before the last slide...
    } else {
      # just assume everything was okay, I don't know what to do about them now
      # get information
      exp_words_displayed         <- TRUE # could see the words?
      exp_colours_distinguishable <- TRUE # could distinguish the colours easily?
      exp_distracted              <- FALSE # was distracted (e.g. by a person, music, a movie)?
      exp_tech_issues             <- "unclear" # were there technical issues (e.g. internet connection crashing)?
    }
    
  }

  # print message
  message(paste(i, " - Reading in file ", file_list[i], ", participant ID: ", id, sep = ""))

  # add column with info on whether participant should be excluded
  excl <- FALSE

  # append to demographics df
  df_demogr <- as.data.frame(rbind(df_demogr,
                                   cbind(id, recording_location, code, prolific_id, confirmation_code,
                                         age, gender, education, handedness,
                                         native_speaker, seeing_impaired,
                                         seeing_impairment_corrected,
                                         drugs, alcohol,
                                         psych_dis, neur_dis, stroke,
                                         medicine, infect_dis,
                                         exp_words_displayed,
                                         exp_colours_distinguishable,
                                         exp_distracted, exp_tech_issues,
                                         excl)))

  # remove helper variables to keep things tidy
  rm (gender, education, handedness,
      native_speaker, seeing_impaired,
      seeing_impairment_corrected, drugs, alcohol,
      psych_dis, neur_dis, stroke, medicine, infect_dis,
      exp_words_displayed, exp_colours_distinguishable,
      exp_distracted, exp_tech_issues,
      row_demogr1, row_demogr2,
      row_exp_check, row_handedness, excl)

  ###########################

  # append information on age & recording location:
  subj_df$age                <- age
  subj_df$recording_location <- recording_location

  # save copy of big df because I'll "shrink" it a bit now
  subj_df_raw <- subj_df
  
  
  ###########################
  
  # GET RAW TEXT & N-BACK DATA

  # get words & information on the text from data
  subj_df     <- subset(subj_df, sender == "word" | sender == "fix_word" | sender == "Stimulus")
  subj_df     <- subj_df[ , c("age", "recording_location", "sender", "word", "duration", 
                              "text_nr","block_kind", "colour", "target", "nback_response", 
                              "nback_RT", "trial_nr", "time_render")]

  # get rid of reading baseline training (that was just a practice block for the participants)
  subj_df     <- subset(subj_df, block_kind != "reading_baseline_training")

  # If the participant repeated one of the n-back training blocks, only look at the second one.
  # Reason: I assume that you only repeat the training if you're not sure you
  #         understood the task correctly the first time.

  # for 1-back training:
  #if (length(which(subj_df$block_kind == "1back_single_training2")) > 0) {
  #  subj_df   <- subset(subj_df, block_kind != "1back_single_training1")
  #}
  # for 2-back training:
  #if (length(which(subj_df$block_kind == "2back_single_training2")) > 0) {
  #  subj_df   <- subset(subj_df, block_kind != "2back_single_training1")
  #}

  ###########################

  ### ADD NUMBERED BLOCK NAMES ####

  # We have each main block twice, but I would like to exclude outliers by block and not by condition.
  # Reason: Reading times in second block might be slightly different than in first block, so don't mix them up.

  # first, just copy the "old" block names
  subj_df$block_names_numbered <- subj_df$block_kind

  # Get all 1-back blocks and call the first 300 trials "1back_main_1". Call the remaining 300 trials "1back_main_2".
  # Do this for Reading BL & 2-back main, too. The single-task blocks don't have to be changed because they're only presented once.
  change_blocknames <- c("Reading_BL_main", "1back_main", "2back_main")

  for (change_block_name in change_blocknames){
    # get the first 300 trials (each block has 300 trials so the first 300 trials = 1st block.
    # There are 2 rows for each trial, which means we need the first 600 rows for the 1st block.)
    subj_df[which(subj_df$block_names_numbered == change_block_name), ]$block_names_numbered[c(1:600)] <- paste(change_block_name,"_1", sep = "")
    subj_df[which(subj_df$block_names_numbered == change_block_name), ]$block_names_numbered           <- paste(change_block_name,"_2", sep = "")
  }

  ## we have to add block numbers for single n-back blocks in lab participants because they did two blocks of each single n-back task
    if (subj_df$recording_location[1] == "lab") {
    
      change_blocknames <- c("1back_single_main", "2back_single_main")
    
      for (change_block_name in change_blocknames){
      # get the first 45 trials
      # There are 2 rows for each trial, which means we need the first 90 rows for the 1st block.)
      
        subj_df[which(subj_df$block_names_numbered == change_block_name), ]$block_names_numbered[c(1:90)] <- paste(change_block_name,"_1", sep = "")
      
        subj_df[which(subj_df$block_names_numbered == change_block_name), ]$block_names_numbered <- paste(change_block_name,"_2", sep = "")
      }
    }

  # Also add block number aka position of the block in the experiment.
  # This way, I can control for tiredness effects.
  unique(subj_df$block_names_numbered)
  # loop block_names_numbered aka individual blocks
  block_nr <-  1
  subj_df$block_nr <- NA
  
  if (subj_df$recording_location[1] == "online") {
  # use all block names you want to get numbers for. I don't care about the training repetitions, but all other blocks get numbers.
    blocks <- c("reading_BL_training", "Reading_BL_main_1",  "Reading_BL_main_2",
                "2back_single_training1", "2back_single_main", "2back_main_1",  "2back_main_2",    
                "1back_single_training1", "1back_single_main", "1back_main_1", "1back_main_2")
    
    for (block in unique(subj_df$block_names_numbered)){
      # if the current block name is one of the main blocks, add block number
      if (block %in% blocks){
        subj_df[which(subj_df$block_names_numbered == block), "block_nr"] <- block_nr
        # go to next block
        block_nr <-  block_nr + 1
      }
    }
  } else if (subj_df$recording_location[1] == "lab") {
    blocks <- c("reading_BL_training", "Reading_BL_main_1",  "Reading_BL_main_2", "2back_single_training1", "2back_single_main_1", "2back_single_main_2", "2back_main_1",  "2back_main_2", "1back_single_training1", "1back_single_main", "1back_single_main_2", "1back_main_1", "1back_main_2")
    
    for (block in unique(subj_df$block_names_numbered)){
      # if the current block name is one of the main blocks, add block number
      if (block %in% blocks){
        subj_df[which(subj_df$block_names_numbered == block), "block_nr"] <- block_nr
        # go to next block
        block_nr <-  block_nr + 1
      }
    }
  }
  
  
  ###########################

  ### COMPUTE READING TIMES ####

  # add durations of fix_word slides and word slides so we get
  # total reading time estimates for each word
  fix_word_durations = subj_df[which(subj_df$sender == "fix_word"), ]$duration
  subj_df[which(subj_df$sender == "word"), ]$duration = subj_df[which(subj_df$sender == "word"), ]$duration + fix_word_durations

  # get rid of fix_word slides so we don't get confused later.
  subj_df <- subset(subj_df, sender != "fix_word")

  # Edit durations aka reading times:
  # If the numbers are saved as strings like this: "234,789"),
  # replace comma by point and typecast to numeric
  #if (class(subj_df$duration) == "character"){
  #  subj_df$duration <- scan(text = subj_df$duration, dec=",", sep=".")
  #} else {
  #  subj_df$duration <- as.numeric(subj_df$duration)
  #}

  # append column with ID of current participant
  subj_df$ID <- id

  ###########################

  ### COMPUTE READING SPEED ####

  # append column with log-transformed reading times
  #subj_df$duration_log <- log(subj_df$duration)

  # append reading speed column (words / 100 s as in Lea's thesis)
  subj_df$reading_speed <- 100 * 1000 / subj_df$duration

  # Explanation for future Merle because for some reason this confuses me every time I stumble upon this:
  # Reading speed is defined as # of words you read / 100 seconds. 
  # Why 100 seconds and not 1 min for example? Unclear.
  # Now we only have the reading time in ms for the current word, so we have to see how 
  # many words we could fit into a period of 100 s (which is 100 * 1000 ms = 100000 ms)
  # assuming we kept this exact pace for each word.
  # To check this, we divide the time interval in ms by the time it took to read 1 word. 
  # The resulting value is the number of words that we could read in 100 s aka the reading speed.
  # reading speed = 100 seconds * 1000 ms / reading time
  
  ###########################
  
  # GET ADDITIONAL INFORMATION ON THE TEXTS:

  ### PUNCTUATION ####

  # Edit the texts a bit. Currently, we have words & punctuation
  # mixed up. Would be nice if we had one word column
  # and some others with info on punctuation.

  punctuation <- c(rep("", times = length(subj_df$ID)))

  # get all .
  punctuation[grep("[.]", subj_df$word)] <- "point"
  # get all ?
  punctuation[grep("[?]", subj_df$word)] <- "question_mark"
  # get all !
  punctuation[grep("[!]", subj_df$word)] <- "exclamation_mark"
  # get all ,
  punctuation[grep("[,]", subj_df$word)] <- "comma"
  # get all ;
  punctuation[grep("[;]", subj_df$word)] <- "semicolon"
  # get all :
  punctuation[grep("[:]", subj_df$word)] <- "colon"

  # get all "
  # This is tricky for various reasons:

  # 1. there could be quotes directly after or
  # before a point for example

  # Idea: Separate column for quotes
  quotes <- c(rep("", times = length(subj_df$ID)))

  # 2. I want to differentiate between opening and closing quotes,
  # but they look the same.

  # Idea: make them all "opening quotes" and change every second one to
  # "closing_quote". This should do the trick.
  quotes[grep("\"", subj_df$word)] <- "opening_quote"
  opening <- TRUE

  # loop list of quotes
  for (x in 1:length(quotes)){
    # get current value in vector "quotes" & current word
    curr_val  <- quotes[x]
    curr_word <- subj_df$word[x]

    if (curr_val == "opening_quote" & # if the current value is not empty
        opening == TRUE & # and we set "opening" to TRUE
        grepl("\"[A-Za-z0-9]+\"", curr_word) == FALSE){ # and there are not 2 quotes around the word

      # leave it as is, next quote is the closing one
      opening <- FALSE

      # if we have a quote, but it has to be a closing one, change it accordingly
    } else if (curr_val == "opening_quote" &
               opening == FALSE &
               grepl("\"[A-Za-z0-9]+\"", curr_word) == FALSE){
      # change value to closing quote
      quotes[x] <- "closing_quote"
      # next quote is the opening one
      opening <- TRUE
      # if it's a quote around a single word, mark as "both"
    } else if (curr_val == "opening_quote" &
               grepl("\"[A-Za-z0-9]+\"", curr_word) == TRUE){
      # change value to both
      quotes[x] <- "both"
    }
  }

  # remove all punctuation
  word_single <- gsub('[[:punct:] ]+',' ', subj_df$word)
  # "trim" away spaces before and after words
  word_single <- trimws(word_single, which = c("left"))
  word_single <- trimws(word_single, which = c("right"))
  # put dashes into spaces between words (words like "ice-cream" for example)
  word_single <- gsub(" ", "-", word_single, fixed = TRUE)


  # get word length for single words
  word_length_single <- nchar(word_single)


  ### N-BACK RESPONSES ####

  # check if we had an n-back reaction while the word was shown
  # create vector with only FALSEs
  reaction <- c(rep(FALSE, times = length(subj_df$ID)))
  # check where in subj_df we have responses (hit or false alarm) and change value in reaction vector to TRUE at that index
  reaction[which(subj_df$nback_response == "hit" | subj_df$nback_response == "false alarm")] <- TRUE

  # do the same for the subj_df_raw dataframe, because we'll need it later
  subj_df_raw$reaction <- FALSE
  # get idx of all rows where n-back response was recorded, mark those as TRUE in the reaction column.
  subj_df_raw[which(subj_df_raw$nback_response == "hit" | subj_df_raw$nback_response == "false alarm"), "reaction"] <- TRUE

  # Then get idx of all rows containing n-back responses again, but this time only of
  # slides where sender == word. We're only looking for the dual-task blocks.
  # Subtract 1 from each idx in this list to get all the slides before. Those should be the "fix_word" slides.
  # Mark the reaction in those slides as TRUE, too. We need them later.
  subj_df_raw[which((subj_df_raw$nback_response == "hit" | subj_df_raw$nback_response == "false alarm") & subj_df_raw$sender == "word") - 1, "reaction"] <- TRUE


  # APPEND NEW COLUMNS
  # append punctuation and quotes column, column with words without punctuation
  # column with length of each the single words and reaction column as
  # additional columns to subj_df:
  subj_df <- data.frame(cbind(subj_df, word_single, punctuation,
                              quotes, word_length_single, reaction))



  ### STOP WORDS, PUNCTUATION, REACTION AND DURATION OF PREVIOUS WORD ####

  # Now also get previous punctuation, previous quotes, previous
  # word and previous duration because why not.
  # First, append empty columns to df:
  subj_df[, c("previous_word", "previous_punctuation", "previous_quotes", "previous_duration", "previous_reaction", "stop_word")] <- ""

  # get list of German stop_words
  stop_words <- stopwords("de", source = "snowball")
  # snowball = stopwords list based on the Snowball stemmer's word lists.
  # --> https://snowballstem.org/texts/introduction.html

  # now loop rows and gradually fill in the empty columns.
  for (idx in 1:length(subj_df$sender)){
    # if it's the first trial of a new block, go to next iteration
    # because in this case we don't have previous data.
    # Also skip the following part if it's a block without text.
    if (subj_df$trial_nr[idx] > 1 && subj_df$sender[idx] == "word"){
      # fill in the missing data by getting the values from the previous trial:
      subj_df$previous_word[idx]        <- subj_df$word_single[idx-1]
      subj_df$previous_punctuation[idx] <- subj_df$punctuation[idx-1]
      subj_df$previous_quotes[idx]      <- subj_df$quotes[idx-1]
      subj_df$previous_duration[idx]    <- subj_df$duration[idx-1]
      subj_df$previous_reaction[idx]    <- subj_df$reaction[idx-1]
    }

    if (subj_df$sender[idx] == "word" && subj_df$word_single[idx] %in% stop_words){
      # check if current word is a stop word or not
      subj_df$stop_word[idx] <- TRUE
    } else if (subj_df$sender[idx] != "Stimulus"){
      subj_df$stop_word[idx] <- FALSE
    }
  }



  ### WORD FREQUENCIES & SURPRISAL SCORES ####

  # Include word frequencies & surprisal scores for each word

  # append "empty" word frequency & surprisal score columns to df
  # to do so, create a vector of column names
  col_names <- c("word_frequency", "surprisal_2", "entropy_2")#,
  # then add "empty" columns to data frame subj_df
  subj_df[, col_names] <- 0

  # loop individual texts
  for (curr_text_nr in unique(subj_df$text_nr)){

    # in some blocks we don't have texts, so skip those
    if (curr_text_nr == ""){
      next
      # if it's a text block, though, assign word frequencies from csv
    } else {
      #print(curr_text_nr) # uncomment this if you'd like to show the texts each participant read

      # get word frequencies for current text nr
      curr_word_freqs <- subset(word_freqs_df, text_nr == curr_text_nr)$word_frequency
      # find out where in the subj_df text the text is located and add the word frequencies there
      subj_df[which(subj_df$text_nr == curr_text_nr),]$word_frequency <- curr_word_freqs

      # Do the same for the surprisal scores.
      curr_surprisals <- subset(surprisal_df, text_nr == curr_text_nr)

      # find out where in the subj_df text the current text nr is located
      curr_row <- which(subj_df$text_nr == curr_text_nr)

      # add the surprisal scores (untransformed & orthogonalized scores) there
      subj_df[curr_row, c("surprisal_2", "entropy_2")]  <- curr_surprisals[c("surprisal_2_words_context", "entropy_2_words_context")]
      #subj_df[curr_row, c("surprisal_1_ortho", "surprisal_2_ortho",
      #                    "surprisal_8_ortho", "surprisal_16_ortho",
      #                    "surprisal_32_ortho")]                     <- curr_surprisals[c("surprisal_1_ortho", "surprisal_2_ortho", "surprisal_8_ortho", "surprisal_16_ortho", "surprisal_32_ortho")]

    }# END if
  }# END loop texts

  
  ### GET SURPRISAL SCORES OF PREVIOUS WORD ####
  # --> basically do the same again as before, but add surprisal scores for current for to row of next word.

  # append "empty" word frequency & surprisal score columns to df
  # to do so, create a vector of column names
  col_names <- c("word_frequency_previous_word", "previous_surprisal_2", "previous_entropy_2")
  # then add "empty" columns to data frame subj_df
  subj_df[, col_names] <- 0

  # loop individual texts
  for (curr_text_nr in unique(subj_df$text_nr)){

    # in some blocks we don't have texts, so skip those
    if (curr_text_nr == ""){
      next
      # if it's a text block, though, assign word frequencies from csv
    } else {
      #print(curr_text_nr) # uncomment this if you'd like to show the texts each participant read

      # get word frequencies for current text nr
      curr_word_freqs <- subset(word_freqs_df, text_nr == curr_text_nr)$word_frequency

      # now this is where we do it differently than before: Remove the last value and add 1 NA
      # at idx = 1 of the vector, so the values are moved by 1 position.
      curr_word_freqs <- c(NA, curr_word_freqs[-length(curr_word_freqs)])

      # find out where in the subj_df text the text is located and add the word frequencies there
      subj_df[which(subj_df$text_nr == curr_text_nr),]$word_frequency_previous_word <- curr_word_freqs

      # Do the same for the surprisal scores:
      curr_surprisals <- subset(surprisal_df, text_nr == curr_text_nr)[ , c("surprisal_2_words_context", "entropy_2_words_context")]

      # add 1 NA to the start of the vectors, remove last value in each
      curr_surprisals <- rbind(c(NA, NA), curr_surprisals[-nrow(curr_surprisals), ])

      # find out where in the subj_df text the current text nr is located
      curr_row <- which(subj_df$text_nr == curr_text_nr)

      # add the surprisal scores (untransformed & orthogonalized scores) there
      subj_df[curr_row, c("previous_surprisal_2", "previous_entropy_2")] <- curr_surprisals

    }# END if
  }# END loop texts


  ### CHANGE ORDER OF DATAFRAME ####
  # I'm not a big fan of the order of the df, so move around the columns a bit:
  col_order <- c("ID", "age", "recording_location", 
                 "sender",  "block_kind", "block_nr", "block_names_numbered",
                 "trial_nr", "text_nr", "word", "duration", "reading_speed",
                 "colour", "target", "time_render", "nback_response", "nback_RT", "reaction",
                 "word_single", "stop_word", "punctuation", "quotes",
                 "word_length_single", "word_frequency",
                 "surprisal_2", "entropy_2", 
                 "previous_surprisal_2", "previous_entropy_2",
                 "word_frequency_previous_word", "previous_word",
                 "previous_punctuation", "previous_quotes",
                 "previous_duration", "previous_reaction")

  subj_df <- subj_df[, col_order]

  
  ###########################
  # GET PERFORMANCE MEASURES:

  ### COMPREHENSION QUESTION PERFORMANCE ####
  # Check the performance in the reading comprehension questions in the 2 baseline blocks:
  # If they don't have 3/3 in at least one of the blocks, exclude their data.

  # We now use the "old" df with all information concerning the questions
  # get question data:
  Q_df <- subset(subj_df_raw, Q1 != "")[,c("Q1", "Q2", "Q3", "text_nr", "block_kind", "ID", "age", "recording_location")]

  # fill ID column with id value
  Q_df$ID <- id

  # For now I don't really care about the answer, I only want to know if they chose the correct one or not.
  # So change labels a bit.

  # yes I know this is a weird approach
  Q_df <- Q_df %>% dplyr::mutate(Q1 = dplyr::recode(Q1, "TRUE_a" = "T", "TRUE_b" = "T", "TRUE_c" = "T", "TRUE_d" = "T",
                                                        "a" = "F", "b" = "F", "c" = "F", "d" = "F"))

  Q_df <- Q_df %>% dplyr::mutate(Q2 = dplyr::recode(Q2, "TRUE_a" = "T", "TRUE_b" = "T", "TRUE_c" = "T", "TRUE_d" = "T",
                                                        "a" = "F", "b" = "F", "c" = "F", "d" = "F"))

  Q_df <- Q_df %>% dplyr::mutate(Q3 = dplyr::recode(Q3, "TRUE_a" = "T", "TRUE_b" = "T", "TRUE_c" = "T", "TRUE_d" = "T",
                                                        "a" = "F", "b" = "F", "c" = "F", "d" = "F"))
  # typecast everything to logical
  Q_df$Q1 <- as.logical(Q_df$Q1)
  Q_df$Q2 <- as.logical(Q_df$Q2)
  Q_df$Q3 <- as.logical(Q_df$Q3)

  # get performance in Qs
  Q_df$nr_correct <- c(rep(NA, times = length(Q_df$Q1)))
  # for each block (= row in this df), count how many questions were answered correctly.
  for (row_idx in 1:length(Q_df$Q1)){
    # count how many Questions were answered correctly in the current block (= row)
    nr_correct <- length(which(Q_df[row_idx,c(1:3)] == TRUE))
    # append to Q_df & subj_df$Q_nr_correct
    Q_df$nr_correct[row_idx] <- nr_correct
  }

  # append Q_df to bigger df for all participants
  df_comprehension_Qs <- as.data.frame(rbind(df_comprehension_Qs, Q_df))


  ### N-BACK PERFORMANCE ####

  # set all durations in n-back trials without response to NA
  # (if no reaction was recorded, the value from the trial before is saved in the df,
  # just a small error in the experiment but nothing unfixable)
  subj_df[which(subj_df$reaction == F), ]$nback_RT <- NA
  # subtract trial onset times (time_render) from the n-back RT values so they make more sense:
  subj_df[which(subj_df$reaction == T), ]$nback_RT <- subj_df[which(subj_df$reaction == T), ]$nback_RT - subj_df[which(subj_df$reaction == T), ]$time_render

  # add the 50ms from the fixed word period to the n-back response times
  # get subset with all fix_word durations from all trials where n-back response was recorded
  fix_word_durations <- subset(subj_df_raw, sender == "fix_word" & reaction == TRUE)$duration

  subj_df[which(subj_df$sender == "word" & subj_df$reaction == T), ]$nback_RT <- subj_df[which(subj_df$sender == "word" & subj_df$reaction == T), ]$nback_RT +
                                                                                 fix_word_durations

  # check n-back performance in each block:
  nback_block_names = c("1back_single_training1", "1back_single_training2", "1back_single_main", "1back_main",
    "2back_single_training1", "2back_single_training2", "2back_single_main", "2back_main")

  # append empty d-prime column to df:
  subj_df$dprime <- c(rep(NA, times = length(subj_df$word)))

  # loop block names:
  for (block_name in nback_block_names){

    # check if block name exists in df:
    if (length(which(unique(subj_df$block_kind) == block_name)) > 0){
      # if so, compute d-primes:

      # get data for current block
      curr_block <- subset(subj_df, block_kind == block_name)

      # remove trials where the RT was way too fast
      # (= participant reacted by accident)
      curr_block <- subset(curr_block, (nback_RT >= 100 | is.na(nback_RT)))

      # if there are still some trials left (let's say at least 10), compute d-prime
      if (length(curr_block$ID) > 10){
        # the main blocks are played twice in the experiment, so separate them
        if (length(curr_block$ID) > 300){
          # get first half, compute d-prime & add to bigger df
          d_prime <- get_dprime(curr_block[c(1:300),]$nback_response)
          subj_df[which(subj_df$block_kind == block_name)[c(1:300)],]$dprime <- d_prime

          # same procedure for the second half
          d_prime <- get_dprime(curr_block[c(301:600),]$nback_response)
          subj_df[which(subj_df$block_kind == block_name)[c(301:600)],]$dprime <- d_prime

          # if there's only one block:
        } else if (length(curr_block$ID) <= 300){
          # do it only once
          d_prime <- get_dprime(curr_block$nback_response)
          subj_df[which(subj_df$block_kind == block_name),]$dprime <- d_prime
        } # END if loop - check if block exists twice
      } # END if loop - check if there are still enough trials left
    } # END if loop - check for block name in df
  }# END loop - compute d-primes
  
  
  # We'll use the mean d-prime from 1-back and 2-back single task main blocks
  # as a working memory measure for each participant. So get mean & append it as a new column to the df.
  
  subj_df$mean_dprime_singletasks <- mean(c(unique(subj_df[which(subj_df$block_kind =="1back_single_main"),]$dprime),
                                            unique(subj_df[which(subj_df$block_kind =="2back_single_main"),]$dprime)))
  
  ###########################

  ### MARK PARTICIPANTS/BLOCKS FOR EXCLUSION:

  # append "empty" exclude trial / exclude participant columns to df
  subj_df$excl_trial       <- FALSE
  subj_df$excl_participant <- FALSE

  
  ### EXCLUDE PARTICIPANT IF THERE WERE TECHNICAL ISSUES ####
  
  # Online studies are a bit unpredictable, so better check everything was displayed &
  # recorded correctly before including datasets.

  # check if durations are in a range that makes sense
  # --> exclude datasets with negative reading times because they should be impossible to achieve.
  # If there are any, I assume there was something off with the measurement and I can't trust any
  # of the other durations in this dataset either.
  
  # For the reading times, I always took the sum of the duration of the word slide and the duration of the fixed 50 ms slide before. 
  # Technically, all RTs should be at least 50ms long, but it's possible that sometimes frames are skipped, 
  # so they could also be shorter, which is why I'm only excluding data that are completely implausible even if all frames were skipped.
  min_duration <- range(subj_df$duration)[1]
  if (min_duration < 0){
    # change value in excl column in df_demogr to TRUE.
    df_demogr$excl[length(df_demogr$excl)] <- TRUE
    # set all values in excl_participant column to TRUE
    #subj_df$excl_participant <- TRUE
    message("     participant was excluded because there were negative values in the reading times - probably a measurement error!")
  }

  # now also check if the participant told us there was something weird going on during the experiment:

  #first print any statements on technical issues in the console. 
  # This was free text input so I have to read them all and check "manually" if everything was okay.
  message(paste("potential technical issues:", df_demogr$exp_tech_issues[i], sep = " "))

  # typecast some column from df_demogr
  df_demogr$exp_words_displayed <- as.logical(df_demogr$exp_words_displayed)
  df_demogr$exp_colours_distinguishable <- as.logical(df_demogr$exp_colours_distinguishable)
  df_demogr$exp_distracted <- as.logical(df_demogr$exp_distracted)
  
  # now check the other experiment check questions:
  # if words were not displayed properly or colours were NOT distinguishable
  if (any(c(df_demogr$exp_words_displayed[length(df_demogr$id)], df_demogr$exp_colours_distinguishable[length(df_demogr$id)]) == FALSE)){ 
    
    # change value in excl column in df_demogr to TRUE.
    df_demogr$excl[length(df_demogr$excl)] <- TRUE
    # set all values in excl_participant column to TRUE
    #subj_df$excl_participant <- TRUE
    message("     participant was excluded because they reported errors during running the experiment")

  # Also exclude them if participant reports they were distracted during the experiment:
  } else if (df_demogr$exp_distracted[length(df_demogr$id)] == TRUE){

    # change value in excl column in df_demogr to TRUE.
    df_demogr$excl[length(df_demogr$excl)] <- TRUE
    # set all values in excl_participant column to TRUE
    #subj_df$excl_participant <- TRUE
    message("     participant was excluded because they reported they were distracted during the experiment")

  }

  ### EXCLUDE SINGLE BLOCKS BASED ON COMPREHENSION QUESTION PERFORMANCE: ####
  
  # Idea: only exclude on block level, don't exclude full datasets because they messed up in 1 condition or so.
  #       The linear mixed models should be able to deal with this.
  
  # loop blocks in Q_df
  for (curr_block_idx in 1:length(Q_df$block_kind)){
    # get question data for current block 
    curr_row <- Q_df[curr_block_idx,]

    # exclude block data if participant answered less than 1/3 questions correctly.

    # check if we have at least 1 correct answer
    # if not, exclude all trials from this block
    if (curr_row$nr_correct < 1){
        # find text nr in subj df and set all values in column excl_trial to TRUE
        subj_df[which(subj_df$text_nr == curr_row$text_nr), "excl_trial"] <- TRUE
        message(paste("1 block was excluded because comprehension Q performance was too low (< 2 / 3 correct). Current condition:", curr_row$block_kind, sep = " "))
    }
      
  }# END FOR LOOP for blocks in Q_df
  

  ### EXCLUDE SINGLE BLOCKS BASED ON N-BACK TASK PERFORMANCE: ####

  # Check blocks with n-back tasks: 
  # Exclude block if the participant didn't do the n-back task (i.e. if they always/never pressed the target button).
  # We're excluding based on the d-prime values.
  # In the dual-task (main) blocks, we always had 50 targets & 250 non-targets. 
  # The d-prime for 0 hits and 0 false alarms is 0. If they always pressed the button and have 50 hits and 250 false alarms, the d-prime is also 0.
  # This means that they should have a d-prime above 0 if they at least attempted to do the task or below 0 if they attempted to do the 
  # task but did it the wrong way around (i.e.reacted if trial was a non-target trial and didn't react if trial was a target trial).
  
  # --> exclude all blocks with d-primes == 0.
  
  message(paste("excluded", length(subj_df[which(subj_df$dprime == 0), "excl_trial"]), "trials because d-prime was 0", sep = " "))
  
  subj_df[which(subj_df$dprime == 0), "excl_trial"] <- TRUE

  
  # If we need to exclude the whole dataset, do it now:
  # Print message if the whole dataset of the current participant was excluded, also print info on recording site & age:
  if (as.logical(df_demogr$excl[length(df_demogr$excl)]) == T){
    
    subj_df$excl_participant <- TRUE
    message("Participant was excluded from further analyses.")
    message(paste("age", as.character(unique(subj_df$age)), ", recording site:", as.character(unique(subj_df$recording_location))))
    
    # Hint: We exclude the whole dataset here by just not appending it to the big df for all 
    #       participants "df_text_data", but we have to mark them as excluded in the demographics df.
    
  } else{
    message("Participant passed all inclusion criteria.")

    # append subj_df chunk to df_text_data where we collect the data of all participants we want to keep
    df_text_data <- as.data.frame(rbind(df_text_data, subj_df))

  }

  message("------------------------")

}# END READ IN DATASETS


# also append d-primes from df_text_data to df_comprehension_Qs:
#df_comprehension_Qs
#df_comprehension_Qs$dprime <- merge(df_comprehension_Qs, df_text_data, by = c("ID", "text_nr"), all.x = TRUE)

# aggregate df_text_data so it has the same length as df_comprehension_Qs
#tmp_df_text_data <- subset(df_text_data, block_kind %in% unique(df_comprehension_Qs$block_kind))

#tmp_df_text_data <- aggregate(tmp_df_text_data$dprime, 
#                              by = list(ID = tmp_df_text_data$ID, text_nr = tmp_df_text_data$text_nr), 
#                              FUN = mean)

#length(tmp_df_text_data$ID)


# exclude all trials that we marked for exclusion:
df_text_data <- subset(df_text_data, excl_trial == FALSE)

# exclude data of participants we excluded from df_comprehension_Qs:
df_comprehension_Qs <- subset(df_comprehension_Qs, !(ID %in% subset(df_demogr, excl == TRUE)$id))

# clean up!

rm(list=ls()[! ls() %in% c("df_text_data", "df_demogr", "df_comprehension_Qs", "word_freqs_df", 
                           "surprisal_df", "blocks","apatheme", "palet_load", 
                           "palet_dprimes", "palet_dprimes_lines", 
                           "palet_lab_online", "palet9", "today")])

```

## Save raw data in folder "RData"
```{r save raw data, echo = FALSE}

# save df
save(df_text_data, file = here::here("Analysis/RData/df_text_data_all_subjects_09_24.RData"))

```

## find & exclude outliers using z-sqrt-POMS-transformation
```{r find and exclude outlier trials, echo = FALSE}

# only use data from the main blocks from now on:
df_text_data_clean <- subset(df_text_data, block_kind == "Reading_BL_main" |
                               block_kind == "1back_main" |
                               block_kind == "2back_main")

message("Nr of trials before exclusion of trials: ", length(df_text_data_clean$ID))

### EXCLUDE BREAKS ####
# --> Exclude all trials where participants took more than 5 seconds (arbitrary value)
#     I don't want breaks to influence the scaling of my "usable" data in the next steps
message(paste(length(subset(df_text_data_clean, duration > 5000)$ID), " trials containing breaks were excluded from further analysis", sep = ""))

df_text_data_clean <- subset(df_text_data_clean, duration <= 5000)

# compare reading time distribution of online & lab data
#plot_reading_times <- df_text_data_clean
#densityplot(subset(plot_reading_times, recording_location == "online")$duration)
#densityplot(subset(plot_reading_times, recording_location == "lab")$duration)
# --> raw reading time data from the lab look better than from online - again you can see that in the lab, people were a bit slower

# Let's check how this looks like if we divide the lab sample by age group (< 60 and >= 60)
#densityplot(subset(plot_reading_times, recording_location == "lab" & age >= 60)$duration)
#densityplot(subset(plot_reading_times, recording_location == "lab" & age < 60)$duration)
# --> looks like older people are slower, but that's not a big surprise 

# Throw both samples together & plot again
#densityplot(plot_reading_times$duration)


### TRANSFORM DATA ####

#range(df_text_data_clean$duration)

# Try outlier exclusion as described in Cousineau & Chartier, 2010
# I found this approach in this paper, where it's recommended as the best outlier exclusion method for skewed data
# https://doi.org/10.3389/fpsyg.2021.675558

# "For each transformed value, the square root of the untransformed value minus the minimum value of the sample divided
# through the sample range is calculated. The fraction bounds all values between 0 and 1,
# while the square root enlarges small values (Cousineau and Chartier, 2010).
# Afterwards, these values are z-transformed and values exceeding a particular z-score (e.g., 2 or 3)
# are excluded. For the present simulations, we excluded RTs associated with a z-score larger/smaller than ±2 as outliers."
# (Berger & Kiefer, 2021)

# Long story short:
# transf_val = sqrt (  ( x - sample_min ) / ( sample_max - sample_min)  )
# --> after this, z-transform all values and exclude all values exceeding a value of ± 2 (or ± 3, but they used 2 in the paper)

# This is basically a POMS (Little (2013), read in Moeller (2013)) transformation where you get
# the square root of the output afterwards and z-transform everything.

# Careful, normally, if you wanted to use the transformed values for group comparisons later, 
# you'd have to to the transformation across participants & conditions, so everything gets "pulled" into the same range.
# If you do this for each subject & condition separately, you can't compare means
# anymore, because every subset of data would have its own scale.

# Here, we only want to use the transformation for identifying & excluding outliers, so we don't really care about this problem. 
# So we can do this on block level, so we don't exclude more trials from "slower" 2-back blocks than from the BL for example.



# create 4 new columns in df_demogr for keeping track of how many trials were excluded per participant & condition.
df_demogr$trials_excluded_BL    <- 0
df_demogr$trials_excluded_1back <- 0
df_demogr$trials_excluded_2back <- 0
df_demogr$trials_excluded_all   <- 0

# create new column in df_text_data_clean for the transformed RTs:
df_text_data_clean$tmp_transformed_RTs <- NA 

# get min reading time
# sample_min <- min(df_text_data$duration)
sample_min <- 0 # use smallest possible value here (this is described in a book by Little, 2013) - in this case: 0 words / 100 ms

# loop participants:
message("start excluding trials (block-wise)")
for (curr_id in unique(df_text_data_clean$ID)){
  
  message("current participant: ", curr_id)
  
  # create placeholders to count excluded trials / condition
  trials_excluded_BL    <- 0
  trials_excluded_1back <- 0
  trials_excluded_2back <- 0
  
  # get data of current participant:
  curr_df <- subset(df_text_data_clean, ID == curr_id)

  # loop blocks:
  for (curr_block in unique(curr_df$block_names_numbered)){
    #message("current block: ", curr_block)
  
    # get data of current block:
    curr_block_data <- subset(curr_df, block_names_numbered == curr_block)

    # get max reading time (use sample maximum here)
    sample_max <- max(curr_block_data$duration)

    # do sqrt(POMS) transform of raw reading time values
    duration_standardized <- sqrt((curr_block_data$duration - sample_min) / (sample_max - sample_min))

    # z-transform reading data
    duration_standardized <- as.vector(scale(duration_standardized, center = T, scale = T))

    # put the transformed values into the big df with data of all participants:
    df_text_data_clean[which(df_text_data_clean$ID == curr_id & 
                             df_text_data_clean$block_names_numbered == curr_block), ]$tmp_transformed_RTs <- duration_standardized
    
    # check how many trials we have that are < -2 or > 2:
    trials_excluded <- length(which(duration_standardized > 2))
    
    # check which kind of block we have here & add nr of excluded trials to counter:
    if (curr_block %in% c("Reading_BL_main_1", "Reading_BL_main_2")){
      df_demogr[which(df_demogr$id == curr_id), ]$trials_excluded_BL    <- df_demogr[which(df_demogr$id == curr_id), ]$trials_excluded_BL    + trials_excluded
    } else if (curr_block %in% c("1back_main_1", "1back_main_2")) {
      df_demogr[which(df_demogr$id == curr_id), ]$trials_excluded_1back <- df_demogr[which(df_demogr$id == curr_id), ]$trials_excluded_1back + trials_excluded
    } else if (curr_block %in% c("2back_main_1", "2back_main_2")) {
      df_demogr[which(df_demogr$id == curr_id), ]$trials_excluded_2back <- df_demogr[which(df_demogr$id == curr_id), ]$trials_excluded_2back + trials_excluded
    } 
    # also add to counter for nr of excluded trials across conditions:
    df_demogr[which(df_demogr$id == curr_id), ]$trials_excluded_all <- df_demogr[which(df_demogr$id == curr_id), ]$trials_excluded_all + trials_excluded
  
  }# END LOOP BlOCKS
} # END LOOP PARTICIPANTS


# get index of all values < - 2 or > 2 & actually exclude those trials from the dataframe
excl_row_idx <- which(df_text_data_clean$tmp_transformed_RTs < -2 | df_text_data_clean$tmp_transformed_RTs > 2)

# check how the corresponding untransformed RTs look like so we get a feeling for what's being excluded:
#densityplot(df_text_data_clean[excl_row_idx, "duration"])

# kick out the outliers:
df_text_data_clean[excl_row_idx, "excl_trial"] <- TRUE
df_text_data_clean <- subset(df_text_data_clean, excl_trial == FALSE)

# drop column with the z-sqrt-POMS-transformed data, we don't need it anymore.  
df_text_data_clean$tmp_transformed_RTs <- NULL


# print some information on how many trials were excluded per recording location, condition, per age group and per condition x age group:

# total number of excluded trials
excl_trials      <- sum(df_demogr$trials_excluded_all)
nr_trials_all    <- 300*2*3 * length(subset(df_demogr, excl == F)$trials_excluded_all)
percent_excluded <- round(excl_trials/nr_trials_all * 100, digits = 3)
message("In total, across recording sites, age groups & conditions, we excluded ", excl_trials, " trials. That's ", percent_excluded, "% of all trials from the main blocks.")

# average across conditions, age groups and recording locations
info_nr_excl_mean <- round(mean(subset(df_demogr, excl == F)$trials_excluded_all), digits = 3)
info_nr_excl_sd   <- round(sd(subset(df_demogr, excl == F)$trials_excluded_all), digits = 3)
message("On average, across recording sites, age groups & conditions, we excluded ", info_nr_excl_mean, " ± ", info_nr_excl_sd, " trials per participant")

# old vs. young across conditions & recording locations:
info_nr_excl_old       <- round(mean(subset(df_demogr, age >= 60 & excl == F)$trials_excluded_all), digits = 3)
info_nr_excl_young     <- round(mean(subset(df_demogr, age <= 30 & excl == F)$trials_excluded_all), digits = 3)
info_nr_excl_middle    <- round(mean(subset(df_demogr, age > 30 & age < 60 & excl == F)$trials_excluded_all), digits = 3)
info_nr_excl_old_sd    <- round(sd(subset(df_demogr, age >= 60 & excl == F)$trials_excluded_all), digits = 3)
info_nr_excl_young_sd  <- round(sd(subset(df_demogr, age <= 30 & excl == F)$trials_excluded_all), digits = 3)
info_nr_excl_middle_sd <- round(sd(subset(df_demogr, age > 30 & age < 60 & excl == F)$trials_excluded_all), digits = 3)
message("On average, across recording sites & conditions, we excluded ", info_nr_excl_old, " ± ", info_nr_excl_old_sd, " trials from older participants aged 60+ as opposed to ", info_nr_excl_middle, " ± ", info_nr_excl_middle_sd, " trials from middle-aged participants aged 31 - 59, and", info_nr_excl_young, " ± ", info_nr_excl_young_sd, " trials from younger participants aged 18 - 30")

# BL vs. 1-back vs. 2-back across age groups & recording locations:
info_nr_excl_BL    <- round(mean(subset(df_demogr, excl == F)$trials_excluded_BL), digits = 3)
info_nr_excl_1back <- round(mean(subset(df_demogr, excl == F)$trials_excluded_1back), digits = 3)
info_nr_excl_2back <- round(mean(subset(df_demogr, excl == F)$trials_excluded_2back), digits = 3)
info_nr_excl_BL_sd    <- round(sd(subset(df_demogr, excl == F)$trials_excluded_BL), digits = 3)
info_nr_excl_1back_sd <- round(sd(subset(df_demogr, excl == F)$trials_excluded_1back), digits = 3)
info_nr_excl_2back_sd <- round(sd(subset(df_demogr, excl == F)$trials_excluded_2back), digits = 3)
message("On average, across age groups & conditions, we excluded ", info_nr_excl_BL, " ± ", info_nr_excl_BL_sd, " trials from the BL condition as opposed to ", info_nr_excl_1back, " ± ", info_nr_excl_1back_sd, " trials from the 1-back and ", info_nr_excl_2back, " ± ", info_nr_excl_2back_sd, " trials from the 2-back task.")

# lab vs. online across conditions & age groups:
info_nr_excl_lab       <- round(mean(subset(df_demogr, recording_location == "lab" & excl == F)$trials_excluded_all), digits = 3)
info_nr_excl_online    <- round(mean(subset(df_demogr, recording_location == "online" & excl == F)$trials_excluded_all), digits = 3)
info_nr_excl_lab_sd    <- round(sd(subset(df_demogr, recording_location == "lab" & excl == F)$trials_excluded_all), digits = 3)
info_nr_excl_online_sd <- round(sd(subset(df_demogr, recording_location == "online" & excl == F)$trials_excluded_all), digits = 3)
message("On average, across age groups & conditions, we excluded ", info_nr_excl_lab, " ± ", info_nr_excl_lab_sd, " trials from lab participants as opposed to ", info_nr_excl_online, " ± ", info_nr_excl_online_sd, " trials from online participants.")


```


## log-transform reading times
```{r log-transform reading times, echo = FALSE}

# Idea: Ignore that we just transformed our reading times for outlier exclusion. 
# We now take the raw reading times again and log-transform them.

# use natural logarithm (base e) here:
df_text_data_clean$reading_times_log <- log(df_text_data_clean$duration)
# to reverse the log transformation and get the data back to the original scale (for easier interpretation of the results), 
# use this: exp(log_transformed_data)

# plot the distribution: 
#densityplot(df_text_data_clean$reading_times_log)

# make sure we update the values in the column previous_duration as well:
df_text_data_clean$previous_reading_times_log <- log(as.numeric(df_text_data_clean$previous_duration))

```


# prepare data for group comparisons
```{r clean up df a bit, echo = TRUE}

# name df differently:
df_clean <- df_text_data_clean

################

# rename "block_kind" column 
names(df_clean)[which(names(df_clean) == "block_kind")] <- "cognitive_load"

# recode values in cognitive_load column
df_clean$cognitive_load <- ifelse(df_clean$cognitive_load == "Reading_BL_main", "BL",
                                  ifelse(df_clean$cognitive_load == "1back_main", "1back",
                                         ifelse(df_clean$cognitive_load == "2back_main", "2back",
                                                df_clean$cognitive_load)))

# turn the values into factors and set their order
df_clean$cognitive_load <- factor(df_clean$cognitive_load,
                                  levels = c("BL", "1back", "2back"))

################

# create new column "age_group" for the 2 age groups.
# older = 60+
# younger = < 60
df_clean$age_group <- ifelse(df_clean$age < 40, "young",
                             ifelse(df_clean$age >= 40 & df_clean$age < 60, "MA",
                                  ifelse(df_clean$age >= 60, "old",
                                                df_clean$age)))
# turn them into factors and make sure the order is young -- old
df_clean$age_group <- factor(df_clean$age_group,
                             levels = c("young", "MA", "old"))

################

# now also create a column for the sample: divide lab - young, lab - middle_aged, lab - old and online:
df_clean$sample <- ifelse(df_clean$age_group == "young" & df_clean$recording_location == "lab", "lab - young",
                          ifelse(df_clean$age_group == "MA" & df_clean$recording_location == "lab", "lab - MA",
                            ifelse(df_clean$age_group == "old" & df_clean$recording_location == "lab", "lab - old",
                                 ifelse(df_clean$recording_location == "online", "online", NA))))

# turn them into factors and make sure the order is online -- lab young -- lab old
df_clean$sample <- factor(df_clean$sample,
                          levels = c("online", "lab - young", "lab - MA", "lab - old"))


################

# create a column for comprehension question performance (% of correct answers)

# merge df_clean and df_comprehension_Qs with the comprehension question scores based on "ID" and "text_nr"
df_clean <- merge(df_clean, df_comprehension_Qs[, c("ID", "text_nr", "nr_correct")], by = c("ID", "text_nr"), all.x = TRUE)

# divide all scores in nr_correct by 3 and multiply by 100 to get percentage of correct answers in each block:
df_clean$nr_correct <- round(df_clean$nr_correct / 3 * 100, digits = 3)

# rename the new column in df_clean accordingly
colnames(df_clean)[colnames(df_clean) == "nr_correct"] <- "compr_Qs_percent_correct"


################

# Turn word frequencies into categories:
# Can I maybe just use the 5% most frequent words and the 5% rarest words?
# And everything in between (just for plotting rare vs high freq)?
word_freqs <- word_freqs_df$word_frequency
highest_word_freq <- range(word_freqs, na.rm = T)[2]

# get lowest and highest 5% of words (ordered by frequency)
lowest_high  <- min(head(sort(word_freqs, decreasing = TRUE), length(word_freqs) * 5/100))
highest_rare <- max(head(sort(word_freqs, decreasing = FALSE), length(word_freqs) * 5/100))
df_clean$word_frequency_cat <- cut(df_clean$word_frequency,
                                   breaks = c(0, highest_rare, lowest_high, highest_word_freq),
                                   labels = c("low", "medium", "high"))

```

## save preprocessed data in RData file in folder Analysis
```{r save preprocessed data, echo = FALSE}

# save df
save(df_clean, file = here::here("Analysis/RData/df_clean_all_subjects_09_24.RData"))

```


# Plots

# Plots demographics
```{r plot data, message=FALSE, warning=FALSE}

# only get data of participants we included in the analyses:
plot_df <- subset(df_demogr, excl == F)
plot_df$age <- as.numeric(plot_df$age)

# Print info on demographics:
percent_female <- round(length(which(plot_df$gender == "f")) / length(plot_df$gender) * 100, digits = 3)
percent_male <- round(length(which(plot_df$gender == "m")) / length(plot_df$gender) * 100, digits = 3)
percent_nonbinary <- round(length(which(plot_df$gender == "d")) / length(plot_df$gender) * 100, digits = 3)

message(paste("Demographics: \n- Total N = ", length(plot_df$gender), 
              ", N online = ", length(which(plot_df$recording_location == "online")), 
              ", N lab = ", length(which(plot_df$recording_location == "lab")), 
              ",\n        N = 3 additional datasets were excluded & are not taken into account here.",
              "\n- Age distribution: ", round(mean(plot_df$age), digits = 3), "±",
                                         round(sd(plot_df$age), digits = 3), " years",
              " \n- Gender distribution: ", percent_female, "% female: ",  
                                            percent_male, ", % male, and ", 
                                            percent_nonbinary, "% non-binary participants 
              across both samples", sep = ""))


# Plot age distribution (by recording location):
plot_age <- ggplot(data = plot_df, 
                   aes(x = age, group = recording_location)) +
                geom_density(aes(y = after_stat(count),
                                 fill = recording_location),
                             adjust = 0.45, 
                             alpha = 0.5) + 
                geom_rug( alpha = 0.2) +
                scale_x_continuous(breaks = scales::pretty_breaks(n = 10), 
                                   limits = c(0, 100)) +
                scale_fill_manual(values = palet_lab_online) +
                labs(y = "# Participants", 
                     x = "Age") +
                apatheme + # remove grey bg and grid lines
                theme(legend.title = element_blank()) + 
                # Hide parts of the density plot between white rectangles where we don't have data.
                # I don't like how they taper off at the edges.
                annotate("rect", 
                         xmin = 0, xmax = min(plot_df$age)-1, ymin = 0.01, ymax = 5,
                         alpha = 1, fill = "white") + 
                annotate("rect", 
                         xmin = max(plot_df$age)+1, xmax = 100, ymin = 0.01, ymax = 5,
                         alpha = 1, fill = "white")
plot_age
# save plot:
ggsave(plot_age, file = here::here(paste0("Plots/age_distr_", today, ".pdf")), width = 5, height = 5)


```


## Plot RTs by Condition, Location & Age (only dual-task blocks)
```{r plot RT by Condition & Age & Location, message = FALSE, warning = FALSE}

# ---- Plot RTs by Age Group & Condition ----
plot_df <- subset(df_clean, reaction == F) # exclude trials where you had a reaction
plot_df <- plot_df %>% 
                    group_by(recording_location, age, ID, cognitive_load) %>% 
                    summarise(mean_rt = mean(duration)) %>% 
                          rename(Location = recording_location, 
                                 Age = age, 
                                 Subject = ID,
                                 Condition = cognitive_load,
                                 Reaction_time = mean_rt)
plot_df$Condition <- factor(plot_df$Condition, levels = c("BL", "1back", "2back"))

# plot RTs across recording locations:
rt_age_log <- ggplot(plot_df, aes(x = Age, y = Reaction_time, color = Condition))+
              geom_point2(alpha = 0.5, size = 1.8) +
              geom_smooth(method = lm, aes(fill = Condition), na.rm = T) +
              scale_color_manual(values = palet_load) +
              scale_fill_manual(values = palet_load) +
              scale_x_continuous(breaks = scales::pretty_breaks(n = 7)) +
              #coord_cartesian(ylim = c(5, 8.4)) +
              labs(y = "log Reading Time") +
              coord_cartesian(ylim = c(NA, 5000)) +
              #                xlim = c(0, 90)) +
              # make y-axis log-transformed (with log base e as in log() function)
              scale_y_log(breaks=c(0, 250, 500, 1000, 2000, 4000), 
                          labels=c("0","250", "500", "1000", "2000", "4000")) +
              apatheme +
              theme(legend.position=("bottom"))

ggsave(rt_age_log, file = here::here(paste0("Plots/RT_age_cond_log_all_", today, ".pdf")), 
       width = 8, height = 5)  

# plot divided by recording location:
rt_age_log_location <- ggplot(plot_df,  
                            aes(x = Age, y = Reaction_time, color = Condition))+
              geom_point2(alpha = 0.5, size = 1.8) +
              geom_smooth(method = lm, aes(fill = Condition), na.rm = T) +
              scale_color_manual(values = palet_load) +
              scale_fill_manual(values = palet_load) +
              scale_x_continuous(breaks = scales::pretty_breaks(n = 7)) +
              labs(y = "log Reading Time") +
              coord_cartesian(ylim = c(NA, 5000)) +
              # make y-axis log-transformed (with log base e as in log() function)
              scale_y_log(breaks=c(0, 250, 500, 1000, 2000, 4000), 
                          labels=c("0","250", "500", "1000", "2000", "4000")) +
              apatheme +
              facet_wrap(~ Location)
              theme(legend.position=("bottom"))
ggsave(rt_age_log_location, 
       file = here::here(paste0("Plots/RT_age_cond_log_location_", today, ".pdf")), 
       width = 8, height = 5)  
```


## Plot d-primes by Condition, Location & Age
Hint: We didn't have an n-back task in the baseline condition, so we can only compute & plot them for the 1-back and 2-back dual- and single-task blocks.
```{r plot d-primes by condition, age and location, echo = TRUE}

# get data, exclude BL because we didn't have an n-back task there
plot_df <- subset(df_clean, cognitive_load != "BL" )

# get d-prime data:
plot_df <- subset(df_text_data, block_kind == "1back_single_main" |
                                block_kind == "2back_single_main" |
                                block_kind == "1back_main" |
                                block_kind == "2back_main")

# aggregate by recording_location, age group, ID and cognitive load condition
plot_df <- setNames(aggregate(plot_df$dprime,
                              by = list(plot_df$ID, plot_df$age, 
                                        plot_df$recording_location, plot_df$block_kind),
                              FUN = mean),
                    c("ID", "Age", "Location", "Condition", "Mean_dprime"))



# plot d-primes in dual- & single-tasks across recording locations
plot_dprimes <- ggplot(plot_df, aes(x = Age, 
                                    y = Mean_dprime, 
                               fill = Condition,
                               color = Condition), 
                            width = 4, height = 7) +
                      #geom_point(aes(color = Condition, fill = Condition), 
                      #       position = position_jitter(width = 0.04, height = 0),
                      #       alpha = 0.3,
                      #       shape = 19,
                      #       size = 1) +
                      geom_smooth(method = lm, aes(fill = Condition, color = Condition), 
                                  na.rm = T, alpha = 0.6) +
                      scale_color_manual(values = palet_dprimes_lines) +
                      scale_fill_manual(values = palet_dprimes) +
                      scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) +
                      apatheme +
                      theme(legend.position=("bottom")) +
                      coord_cartesian(ylim = c(0, 5))
ggsave(plot_dprimes, file = here::here(paste0("Plots/dprimes_", today, ".pdf")), 
       device = "pdf", width = 4, height = 4)

# plot d-primes in dual- & single-tasks, divided by location
plot_dprimes_location <- ggplot(plot_df, aes(x = Age, 
                                             y = Mean_dprime, 
                                             fill = Condition,
                                             color = Condition), 
                                width = 4, height = 7) +
                      #geom_point(aes(color = Condition, fill = Condition), 
                      #           position = position_jitter(width = 0.04, height = 0),
                      #           alpha = 0.3,
                      #           shape = 19,
                      #           size = 1) +
                      geom_smooth(method = lm, 
                                  aes(fill = Condition, color = Condition), 
                                  na.rm = T, 
                                  alpha = 0.6) +
                      scale_color_manual(values = palet_dprimes_lines) +
                      scale_fill_manual(values = palet_dprimes) +
                      scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) +
                      apatheme +
                      facet_wrap(~ Location) +
                      theme(legend.position=("bottom")) +
                      coord_cartesian(ylim = c(0, 5))

ggsave(plot_dprimes_location, file = here::here(paste0("Plots/dprimes_location_", today, ".pdf")), 
       device = "pdf", width = 8, height = 4)

  
```

## plot comprehension question performance
--> once across recording locations and once divided by sample
```{r plot comprehension question performance by condition, age and location, echo = FALSE}

# Problem here: I excluded all blocks with comprehension questions scores of 0, 
# so if I plot only the cleaned data, the results will look different.
# --> To do: Plot raw data from df_comprehension_Qs here
# which(df_comprehension_Qs$nr_correct == 0)

plot_df <- df_comprehension_Qs

# quickly rename "block_kind" column:
names(plot_df)[which(names(plot_df) == "block_kind")] <- "cognitive_load"

# exclude training:
plot_df <- subset(plot_df, cognitive_load != "reading_baseline_training")

# recode & order levels of cognitive_load:
plot_df$cognitive_load <- ifelse(plot_df$cognitive_load == "Reading_BL_main", "BL",
                                          ifelse(plot_df$cognitive_load == "1back_main", "1back",
                                              ifelse(plot_df$cognitive_load == "2back_main", "2back",
                                                     plot_df$cognitive_load)))
plot_df$cognitive_load <- factor(plot_df$cognitive_load,
                                             levels = c("BL", "1back", "2back"))

# aggregate by recording_location, age, ID and cognitive load condition
plot_df <- setNames(aggregate(plot_df$nr_correct,
                              by = list(plot_df$ID, plot_df$age, 
                                        plot_df$recording_location, plot_df$cognitive_load),
                              FUN = mean),
                    c("ID", "Age", "Location", "Condition", "Mean_percent_correct"))

# divide nr_correct column values by 3 to get % correct instead of # correct
plot_df$Mean_percent_correct <- plot_df$Mean_percent_correct / 3

# plot % correct by condition & age
plot_comprehensionQs <- ggplot(plot_df,
                               aes(x = Age, 
                                   y = Mean_percent_correct, 
                                   fill = Condition, 
                                   color = Condition), 
                                   width = 4, height = 7) +
                        # not really informative here:
                        #geom_point(aes(color = Condition, fill = Condition), 
                        #     alpha = 0.3,
                        #     shape = 19,
                        #     size = 1) +
                         geom_smooth(method = lm, aes(fill = Condition), na.rm = T) +
                         scale_color_manual(values = palet_load) +
                         scale_fill_manual(values = palet_load) +
                         scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) +
                         apatheme +
                         coord_cartesian(ylim = c(0, 1),
                                         xlim = c(18, 85)) +
                         theme(legend.position = "bottom")
            
ggsave(plot_comprehensionQs, 
       file = here::here(paste0("Plots/compr_Qs_", today, ".pdf")), 
       device = "pdf", width = 4, height = 4)


# plot % correct by condition. location & age
plot_comprehensionQs_location <- ggplot(plot_df,
                               aes(x = Age, 
                                   y = Mean_percent_correct, 
                                   fill = Condition, 
                                   color = Condition), 
                                   width = 4, height = 7) +
                        # not really informative here:
                        #geom_point(aes(color = Condition, fill = Condition), 
                        #     alpha = 0.3,
                        #     shape = 19,
                        #     size = 1) +
                         geom_smooth(method = lm, aes(fill = Condition), na.rm = T) +
                         scale_color_manual(values = palet_load) +
                         scale_fill_manual(values = palet_load) +
                         scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) +
                         facet_wrap(~ Location) +
                         apatheme +
                         coord_cartesian(ylim = c(0, 1),
                                         xlim = c(18, 85)) +
                         theme(legend.position = "bottom")
            
ggsave(plot_comprehensionQs_location, 
       file = here::here(paste0("Plots/compr_Qs_location_", today, ".pdf")), 
       device = "pdf", width = 8, height = 4)


```

# Additional plots: Plot Reading Time by Task (1- and 2-back Dual- and Single-Tasks)
--> once divided by recording location and once across recording locations
```{r plot RTs by task and age, message = FALSE, warning = FALSE}

# get d-prime data:
plot_df <- subset(df_text_data, block_kind == "1back_single_main" |
                                block_kind == "2back_single_main" |
                                block_kind == "1back_main" |
                                block_kind == "2back_main")

# aggregate by recording_location, age group, ID and cognitive load condition
plot_df <- setNames(aggregate(plot_df$duration,
                              by = list(plot_df$ID, plot_df$age, 
                                        plot_df$recording_location, plot_df$block_kind),
                              FUN = mean),
                    c("ID", "Age", "Location", "Condition", "Mean_RT"))

# plot RTs in dual- & single-tasks -- divide by recording location
plot_RT_by_task_location <- ggplot(plot_df, aes(x = Age, 
                                                y = Mean_RT, 
                                                fill = Condition,
                                                color = Condition), 
                                             width = 4, height = 7) +
                              # not really helpful here:
                              #geom_point(aes(color = Condition, fill = Condition), 
                              #       position = position_jitter(width = 0.04, height = 0),
                              #       alpha = 0.3,
                              #       shape = 19,
                              #       size = 1) +
                              geom_smooth(method = lm, 
                                          aes(fill = Condition, color = Condition), 
                                          na.rm = T, alpha = 0.6) +
                              scale_color_manual(values = palet_dprimes_lines) +
                              scale_fill_manual(values = palet_dprimes) +
                              scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) +
                              facet_wrap(~ Location) +
                              apatheme +
                              coord_cartesian(ylim = c(480, 2700),
                                              xlim = c(18, 85)) +
                              # make y-axis log-transformed (with log base e as in log() function)
                              scale_y_log(breaks=c(500, 1000, 1500, 2000, 2500, 3000), 
                                          labels=c("500", "1000", "1500", "2000", "2500", "3000")) +
                              theme(legend.position = "bottom")
ggsave(plot_RT_by_task_location, file = here::here(paste0("Plots/RT_by_task_location_", today, ".pdf")), 
       device = "pdf", width = 8, height = 4)


# Do the same again, but don't split by recording location: 
plot_RT_by_task <- ggplot(plot_df, aes(x = Age, 
                                       y = Mean_RT, 
                                       fill = Condition,
                                       color = Condition), 
                                       width = 4, height = 7) +
                   # not really helpful here:
                   #geom_point(aes(color = Condition, fill = Condition), 
                   #       position = position_jitter(width = 0.04, height = 0),
                   #       alpha = 0.3,
                   #       shape = 19,
                   #       size = 1) +
                   geom_smooth(method = lm, 
                               aes(fill = Condition, color = Condition), 
                               na.rm = T, alpha = 0.6) +
                   scale_color_manual(values = palet_dprimes_lines) +
                   scale_fill_manual(values = palet_dprimes) +
                   scale_x_continuous(breaks = scales::pretty_breaks(n = 10)) +
                   apatheme +
                   coord_cartesian(ylim = c(480, 2700),
                                   xlim = c(18, 85)) +
                   # make y-axis log-transformed (with log base e as in log() function)
                   scale_y_log(breaks = c(500, 1000, 1500, 2000, 2500, 3000), 
                               labels = c("500", "1000", "1500", "2000", "2500", "3000")) +
                   theme(legend.position = "bottom")
plot_RT_by_task
ggsave(plot_RT_by_task, file = here::here(paste0("Plots/RT_by_task_", today, ".pdf")), 
       device = "pdf", width = 4, height = 4)


```



# Stats
## prepare data for LMMs
```{r plot d-primes, echo = FALSE}

######### Linear mixed models #########

# shrink the df a bit: exclude rows that don't have surprisal scores on all time scales
lmm_df <- subset(df_clean, !is.na(surprisal_2))

# create a Simple Coding scheme for the variable cognitive_load
# https://stats.oarc.ucla.edu/r/library/r-library-contrast-coding-systems-for-categorical-variables/
# creating the contrast matrix manually by modifying the dummy coding scheme
c <- contr.treatment(3) # create dummy coding scheme
my.coding <- matrix(rep(1/3, 6), ncol = 2) # make matrix with only 1/3 values
# change values in dummy coding scheme to either -1/3 or 2/6 by
# subtracting 1/3 from 0s and 1s in the dummy coding scheme
my.simple <- c-my.coding
# show new coding scheme
#my.simple

# Explanation for future Merle on why we don't 
# just use the dummy coding scheme: 
# Assume you assigned a coding scheme to variable a. 
# For interpreting main effects of variables a and b, it doesn't make a 
# difference if you use a dummy or simple coding scheme.
# But when you include an interaction of variables a and b, the interpretation of the 
# main effect a changes depending on the coding scheme:
# With the simple coding scheme, the meaning of the main effect a is as usual, 
# but when you use the dummy coding scheme, suddenly the main effect of 
# variable a is interpreted as the change is variable b = 0. 
# Long story short: It's easiest to just always use simple coding.


#assign the new coding scheme to lmm_df$cognitive_load
contrasts(lmm_df$cognitive_load) <- my.simple

# typecast "reaction" to factor because sjplot complains about logicals
# --> I tried just typecasting it to "TRUE" and "FALSE" as factor strings, but for some reason 
# it got converted to logicals again. 
# So I recoded the factor levels as 1 and -1 (aka factor ints) and hope it doesn't get converted again 
lmm_df$reaction <- as.factor(lmm_df$reaction)
#lmm_df$reaction <- as.factor(ifelse(lmm_df$reaction == "TRUE", 1, -1)) # 1 = TRUE and -1 = FALSE

# typecast word_length_single, block_nr, trial_nr & age to numeric, and ID & text_nr to factor
lmm_df$word_length_single <- as.numeric(lmm_df$word_length_single)
lmm_df$trial_nr <- as.numeric(lmm_df$trial_nr)
lmm_df$block_nr <- as.numeric(lmm_df$block_nr)
lmm_df$age <- as.numeric(lmm_df$age)

# ----------- Fix missing d-prime data in BL block -----------
# Problem: I can't include a predictor that doesn't have any data in one of the groups. 
# But I don't have any d-primes for the BL condition because there was no n-back 
# in those blocks, so I have 2 options: Invent data for the BL block & be careful with interpretation, or exclude the d-primes entirely from my model, which would be sad because I want to control for speed-accuracy tradeoff effects. 

# Idea: If d-prime is high, n-back accuracy is high and reading times should be slower.
# So in the BL condition with super fast reading, d-primes should be low if there was an imaginary n-back task in those blocks. 
# Idea: In order not to destroy the direction of the effect, use participant-level mean of all d-primes a constant in all BL blocks.
# We basically fit a regression line for the effect, which will go through the mean in any way, right? So use the mean as the constant for BL.

# try using participant-level mean of d-primes in 1-back and 2-back blocks as constant

# loop participants in lmm_df, get mean d-prime and assign it as constant: 
for (curr_id in unique(lmm_df$ID)){
  
  # get data of current participant
  curr_participant <- subset(lmm_df, ID == curr_id)
  
  # get mean d-prime from all blocks where we don't have NAs (which are the 1-back and 2-back blocks)
  mean_dprime <- mean(curr_participant$dprime, na.rm = T)
  
  # assign mean d-prime as constant in the BL blocks:
  lmm_df[which(lmm_df$ID == curr_id & lmm_df$cognitive_load == "BL"), ]$dprime <- mean_dprime
}

# check if we still have NAs somewhere:
# which(is.na(subset(lmm_df, cognitive_load == "BL")$dprime))


# ----------- prepare columns to check for speed accuracy tradeoff effects -----------

# Further ideas concerning speed accuracy tradeoffs:

# Single participants could perform worse in the n-back than others, so we should have 1 mean d-prime value for each participant.
# Likewise it is possible that participants perform differently in different blocks, 
# e.g. they put more effort into doing the n-back in block 1 and then not so much anymore in block 2. So we also need d-primes on block-level.
# To get rid of the participant-level effect, we need to subtract the mean from each block-wise d-prime though. 
# So what we're doing now is creating 2 new columns with d-prime values: 
# 1. a mean d-prime for each participant
# 2. the deviation of each d-prime from the participant's mean for each block

# 1. calculate mean d-prime for each participant
#lmm_df$dprime_mean <- ave(lmm_df$dprime, lmm_df$ID, FUN = function(x) mean(x, na.rm = TRUE))

# 2. subtract participant mean from each block's original d-prime
#lmm_df$dprime_diff <- lmm_df$dprime - lmm_df$dprime_mean


# Do the same for the comprehension questions:

# 1. calculate mean %correct score for each participant
lmm_df$compr_Qs_percent_correct_mean <- ave(lmm_df$compr_Qs_percent_correct, lmm_df$ID, FUN = function(x) mean(x, na.rm = TRUE))

# 2. subtract participant mean from each block's original %correct score
lmm_df$compr_Qs_percent_correct_diff <- lmm_df$compr_Qs_percent_correct - lmm_df$compr_Qs_percent_correct_mean


# ----------- z-transform continuous variables for mixed models -----------

# Define columns you want to z-transform:

# z-transform: now you can compare the estimates in the lmm output
# only center, not z-transform: units stay the same, makes the interpretation of estimates easier, but you can't compare the estimates anymore.
#--> you could run the models twice, once with z-transformed values (for comparison of effects), once with centered values (for interpretation of single effects)
freq_length_cols <- c("word_frequency", "word_length_single", 
                      "dprime", #"dprime_mean", "dprime_diff", 
                      "previous_reading_times_log",
                      "compr_Qs_percent_correct", "compr_Qs_percent_correct_mean", 
                      "compr_Qs_percent_correct_diff", 
                      "mean_dprime_singletasks",
                      "age")
surprisal_cols   <- c("surprisal_2", "previous_surprisal_2", "entropy_2", "previous_entropy_2") # columns: surprisal_X with X being each of the TSs

# Apply scale function to each column
# --> set center to TRUE to subtract the sample mean from each value, set scale to TRUE to divide by standard deviation
# --> make sure to convert the data to vector format before adding them as a new column
lmm_df[paste0(freq_length_cols, "_z")] <- lapply(lmm_df[freq_length_cols], 
                                                 function(x) as.vector(scale(x, 
                                                                             center = TRUE, 
                                                                             scale = TRUE)))
lmm_df[paste0(surprisal_cols, "_z")] <- lapply(lmm_df[surprisal_cols], 
                                               function(x) as.vector(scale(x, 
                                                                           center = TRUE, 
                                                                           scale = TRUE)))

lmm_df[paste0(freq_length_cols, "_centered")] <- lapply(lmm_df[freq_length_cols], 
                                                        function(x) as.vector(scale(x, 
                                                                                    center = TRUE, 
                                                                                    scale = FALSE)))
lmm_df[paste0(surprisal_cols, "_centered")] <- lapply(lmm_df[surprisal_cols], 
                                                      function(x) as.vector(scale(x, 
                                                                                  center = TRUE, 
                                                                                  scale = FALSE)))

```


## save data
```{r save lmm_df, echo = FALSE}

# save df
save(lmm_df, file = here::here("Analysis/RData/lmm_df_all_subjects_09_24.RData"))

# also save dfs with demographical data and comprehension question data:
save(df_demogr, file = here::here("Analysis/RData/df_demogr.RData"))
save(df_comprehension_Qs, file = here::here("Analysis/RData/df_comprehension_Qs.RData"))


```


# Set up model for each time scale and run
# Linear Mixed Model for log-transformed RT
```{r}
m_RT_ts2_age_centered_random_slope <- lmer(log(duration) ~ # control carry-over effects from previous trials:
                                                           previous_reading_times_log_centered +
                                                           # control diff. response strategies 
                                                           # on block- and participant-level:
                                                           dprime_centered + 
                                                           mean_dprime_singletasks_centered +
                                                           compr_Qs_percent_correct_mean_centered +
                                                           compr_Qs_percent_correct_diff_centered + 
                                                           # lab vs. online:
                                                           recording_location + 
                                                           # properties of words: 
                                                           word_frequency_centered + 
                                                           word_length_single_centered +
                                                           # was there an n-back response in the trial?
                                                           reaction + 
                                                           # position of trial in experiment for 
                                                           # controlling training & tiredness effects:
                                                           block_nr + trial_nr +
                                                           # Surprisal on TS 1, age & cognitive load condition:
                                                           # main effects & their 2-way and 3-way interactions 
                                                           surprisal_2_centered * age_centered * cognitive_load + 
                                                           # subject-specific random slope of cognitive load:
                                                           # cognitive load could have different 
                                                           # effects on different participants
                                                           (1 + cognitive_load | ID) + 
                                                           # random slopes for text, word and colour, 
                                                           # because we picked them "randomly" from a 
                                                           # billion of possible other texts, words and colours
                                                           (1 | text_nr) + 
                                                           (1 | word) + 
                                                           (1 | colour), 
                                                           data = lmm_df, REML = TRUE, 
                                                           # choose bobyqa optimizer 
                                                           # (= Bound Optimization BY Quadratic Approximation) 
                                                           # for estimating model parameters. 
                                                           # It's efficient (= good for large datasets & 
                                                           # complex models) and relatively conservative.
                                                           lmerControl(optimizer = "bobyqa"))

#--- model with entropy scores ----
# performs better and should be our new model
m_RT_ts2_age_centered_random_slope_entropy <- lmer(log(duration) ~ # control carry-over effects from previous trials:
                                                           previous_reading_times_log_centered +
                                                           # control diff. response strategies 
                                                           # on block- and participant-level:
                                                           dprime_centered + 
                                                           mean_dprime_singletasks_centered +
                                                           compr_Qs_percent_correct_mean_centered +
                                                           compr_Qs_percent_correct_diff_centered + 
                                                           # lab vs. online:
                                                           recording_location + 
                                                           # properties of words: 
                                                           word_frequency_centered + 
                                                           word_length_single_centered +
                                                           # was there an n-back response in the trial?
                                                           reaction + 
                                                           # position of trial in experiment for 
                                                           # controlling training & tiredness effects:
                                                           block_nr + trial_nr +
                                                           # entropy
                                                           entropy_2_centered + 
                                                           # Surprisal, age & cognitive load condition:
                                                           # main effects & their 2-way and 3-way interactions 
                                                           surprisal_2_centered * age_centered * cognitive_load + 
                                                           # subject-specific random slope of cognitive load:
                                                           # cognitive load could have different 
                                                           # effects on different participants
                                                           (1 + cognitive_load | ID) + 
                                                           # random slopes for text, word and colour, 
                                                           # because we picked them "randomly" from a 
                                                           # billion of possible other texts, words and colours
                                                           (1 | text_nr) + 
                                                           (1 | word) + 
                                                           (1 | colour), 
                                                           data = lmm_df, REML = TRUE, 
                                                           # choose bobyqa optimizer 
                                                           # (= Bound Optimization BY Quadratic Approximation) 
                                                           # for estimating model parameters. 
                                                           # It's efficient (= good for large datasets & 
                                                           # complex models) and relatively conservative.
                                                           lmerControl(optimizer = "bobyqa"))

# save model output:
saveRDS(m_RT_ts2_age_centered_random_slope_entropy, 
        file = "Analysis/RData/Mixed_models/m_RT_ts2_age_centered_random_slope_entropy.rds")

# Compare models
anova(m_RT_ts2_age_centered_random_slope, m_RT_ts2_age_centered_random_slope_entropy) # The model with entropy is better than the one without

## also run a version without mean-centering age for Johnson Neyman plots
m_RT_ts2_No_centering_age <- lmer(log(duration) ~ previous_reading_times_log_centered + 
                                                  dprime_centered + 
                                                  mean_dprime_singletasks_centered + 
                                                  compr_Qs_percent_correct_mean_centered +
                                                  compr_Qs_percent_correct_diff_centered + 
                                                  recording_location + word_frequency_centered +
                                                  word_length_single_centered + reaction + 
                                                  block_nr + trial_nr + 
                                                  entropy_2_centered +
                                                  surprisal_2_centered * age * cognitive_load + 
                                                  (1 + cognitive_load | ID) + (1 | text_nr) + 
                                                  (1 | word) + (1 | colour), 
                                                  data = lmm_df, REML = TRUE, lmerControl(optimizer = "bobyqa"))
saveRDS(m_RT_ts2_No_centering_age, 
        file = "Analysis/RData/Mixed_models/m_RT_ts2_No_centering_age_random_slope_entropy.rds")

#---- Comparing 1-back to 2-back and not only to reading baseline via post-hoc test ----
test_predictions(m_RT_ts2_age_centered_random_slope_entropy, terms = "cognitive_load [1back, 2back]")

# plotting the difference
pred <- predict_response(m_RT_ts2_age_centered_random_slope_entropy, terms = "cognitive_load [1back, 2back]")
plot(pred)
```




# Comparing 1-back to 2-back instead of to Reading Only
```{r Control Analysis}

# 1st approach: This is just a post-hoc contrast of load 1-back vs. 2-back, but I think that just tells us something about the main effect of load. However, in the LMM, we also have significant 2-way and 3-way interactions of load with surprisal and age, and I would also be interested in how those look like without the Reading Only baseline. 


#---- Comparing 1-back to 2-back and not only to reading baseline via post-hoc test ----
test_predictions(m_RT_ts2_age_centered_random_slope_entropy, terms = "cognitive_load [1back, 2back]")

# plotting the difference
pred <- predict_response(m_RT_ts2_age_centered_random_slope_entropy, terms = "cognitive_load [1back, 2back]")
plot(pred)


# 2nd approach: Create another, simplified LMM with just 2-back vs. 1-back for cognitive load. 

# only look at 1-back and 2-back, because there was no n-back task in the BL condition.
lmm_df_control <- subset(lmm_df, cognitive_load != "BL")
# drop unused load levels (aka "BL")
lmm_df_control$cognitive_load <- droplevels(lmm_df_control$cognitive_load)
# assign simple coding scheme for the 2 cognitive load levels:
lmm_df_control$cognitive_load <- as.factor(lmm_df_control$cognitive_load)
c <- contr.treatment(2) # create dummy coding scheme
my.coding <- matrix(rep(1/2, 2), ncol = 1) # make matrix 
my.simple <- c-my.coding
contrasts(lmm_df_control$cognitive_load) <- my.simple

# fit LMM again:
m_RT_ts2_age_centered_1back_2back <- lmer(log(duration) ~ previous_reading_times_log_centered + 
                                                  dprime_centered + 
                                                  mean_dprime_singletasks_centered + 
                                                  compr_Qs_percent_correct_mean_centered +
                                                  compr_Qs_percent_correct_diff_centered + 
                                                  recording_location + word_frequency_centered +
                                                  word_length_single_centered + reaction + 
                                                  block_nr + trial_nr + 
                                                  entropy_2_centered +
                                                  surprisal_2_centered * age_centered * cognitive_load + 
                                                  (1 + cognitive_load | ID) + (1 | text_nr) + 
                                                  (1 | word) + (1 | colour), 
                                                  data = lmm_df_control, REML = TRUE, lmerControl(optimizer = "bobyqa"))
saveRDS(m_RT_ts2_age_centered_1back_2back, 
        file = "Analysis/RData/Mixed_models/m_RT_ts2_age_centered_1back_2back.rds")

# show results:
tab_model(m_RT_ts2_age_centered_1back_2back, 
          seed = 42,
          show.se = TRUE, 
          show.stat = TRUE,
          show.intercept = FALSE, 
          show.df = FALSE,
          show.re.var = FALSE,
          show.icc = TRUE,
          show.obs = FALSE,
          p.style = "scientific",
          p.threshold = c(0.05), # star after all p-values < 0.05
          p.adjust = "fdr", # NULL
          df.method = "satterthwaite",
          digits = 6, 
          digits.p = 3)


```



# Only test online sample for comparing with the replication sample
```{r Replication Analysis LMM for Online Sample}

# only look at online participants, because we don't have lab participants in the replication sample:
lmm_df_online <- subset(lmm_df, recording_location == "online")

# fit LMM again, this time without the "recording_location" predictor
m_RT_ts2_age_centered_online_sample <- lmer(log(duration) ~ previous_reading_times_log_centered + 
                                                  dprime_centered + 
                                                  mean_dprime_singletasks_centered + 
                                                  compr_Qs_percent_correct_mean_centered +
                                                  compr_Qs_percent_correct_diff_centered + 
                                                  word_frequency_centered +
                                                  word_length_single_centered + reaction + 
                                                  block_nr + trial_nr + 
                                                  entropy_2_centered +
                                                  surprisal_2_centered * age_centered * cognitive_load + 
                                                  (1 + cognitive_load | ID) + (1 | text_nr) + 
                                                  (1 | word) + (1 | colour), 
                                                  data = lmm_df_online, REML = TRUE, lmerControl(optimizer = "bobyqa"))
saveRDS(m_RT_ts2_age_centered_online_sample, 
        file = "Analysis/RData/Mixed_models/m_RT_ts2_age_centered_online_sample.rds")

# show results:
tab_model(m_RT_ts2_age_centered_online_sample, 
          seed = 42,
          show.se = TRUE, 
          show.stat = TRUE,
          show.intercept = FALSE, 
          show.df = FALSE,
          show.re.var = FALSE,
          show.icc = TRUE,
          show.obs = FALSE,
          p.style = "scientific",
          p.threshold = c(0.05), # star after all p-values < 0.05
          p.adjust = "fdr", # NULL
          df.method = "satterthwaite",
          digits = 6, 
          digits.p = 3)



# Do the same for the replication data:

# fit LMM again
m_RT_ts2_age_centered_replication_sample <- lmer(log(duration) ~ previous_reading_times_log_centered + 
                                                  dprime_centered + 
                                                  mean_dprime_singletasks_centered + 
                                                  compr_Qs_percent_correct_mean_centered +
                                                  compr_Qs_percent_correct_diff_centered + 
                                                  word_frequency_centered +
                                                  word_length_single_centered + reaction + 
                                                  block_nr + trial_nr + 
                                                  entropy_2_centered +
                                                  surprisal_2_centered * age_centered * cognitive_load + 
                                                  (1 + cognitive_load | ID) + (1 | text_nr) + 
                                                  (1 | word) + (1 | colour), 
                                                  data = replication_lmm_df, REML = TRUE, lmerControl(optimizer = "bobyqa"))
saveRDS(m_RT_ts2_age_centered_replication_sample, 
        file = "Analysis/RData/Mixed_models/m_RT_ts2_age_centered_replication_sample.rds")

# show results:
tab_model(m_RT_ts2_age_centered_replication_sample, 
          seed = 42,
          show.se = TRUE, 
          show.stat = TRUE,
          show.intercept = FALSE, 
          show.df = FALSE,
          show.re.var = FALSE,
          show.icc = TRUE,
          show.obs = FALSE,
          p.style = "scientific",
          p.threshold = c(0.05), # star after all p-values < 0.05
          p.adjust = "fdr", # NULL
          df.method = "satterthwaite",
          digits = 6, 
          digits.p = 3)


# TO DO: Add plots with estimates & CI as in Malte's paper.
# Explanation for future Merle: We don't compare the results directly with the results from the Full OG LMM because the model comprised the recording_location term there, so it's not 100% comparable. 

plot_estimates_OG <- plot_model(m_RT_ts2_age_centered_online_sample, 
                             terms = c("age_centered",
                                       "surprisal_2_centered", 
                                       "cognitive_load2", 
                                       "cognitive_load3", 
                                       "age_centered:cognitive_load2",                                                       "age_centered:cognitive_load3",
                                       "surprisal_2_centered:age_centered",
                                       "surprisal_2_centered:cognitive_load2",                                                "surprisal_2_centered:cognitive_load3",
                                  "surprisal_2_centered:age_centered:cognitive_load2", "surprisal_2_centered:age_centered:cognitive_load3"), 
                             type = "est",  # Plotting the estimates
                             show.values = FALSE,  # Show the estimate values
                             show.p = TRUE,  # Show p-values next to estimates
                             ci.lvl = 0.95,  # 95% confidence intervals
                             vline.color = "black",  # Solid 0 line
                             dot.size = 2,  # Size of the dots for estimates
                             line.size = 1.5,  # Thickness of the whiskers
                             title = "Estimates and Confidence Intervals",
                             colors = "Set2") +  # Customize colors
                ylim(-0.01, 0.01) +
                theme_minimal() +  # Minimal theme
                theme(axis.line.y = element_line(color = "black"))  # Y-axis line


plot_estimates_replication <- plot_model(m_RT_ts2_age_centered_replication_sample,
                             terms = c("age_centered",
                                       #"surprisal_2_centered", 
                                       #"cognitive_load2", 
                                       #"cognitive_load3", 
                                       "age_centered:cognitive_load2",   
                                       "age_centered:cognitive_load3"#,
                                       #"surprisal_2_centered:age_centered",
                                       #"surprisal_2_centered:cognitive_load2",                                                "surprisal_2_centered:cognitive_load3"#,
                                  #"surprisal_2_centered:age_centered:cognitive_load2", "surprisal_2_centered:age_centered:cognitive_load3"
                                  ), 
                             type = "est",  # Plotting the estimates
                             show.values = FALSE,  # Show the estimate values
                             show.p = TRUE,  # Show p-values next to estimates
                             ci.lvl = 0.95,  # 95% confidence intervals
                             vline.color = "black",  # Solid 0 line
                             dot.size = 2,  # Size of the dots for estimates
                             line.size = 1.5,  # Thickness of the whiskers
                             title = "Estimates and Confidence Intervals",
                             colors = "Set2") +  # Customize colors
                ylim(-0.01, 0.012) +
                theme_minimal() +  # Minimal theme
                theme(axis.line.y = element_line(color = "black"))  # Y-axis line



# TO DO: It's really difficult to plot estimates that differ so much. Maybe 2 panels for big and small effects? I think the simple slopes plots would just be confusing. Or could I plot the deviation between estimates?!



```



# Generalized Additive Mixed Model (GAM)
```{r GAM}

# First make sure there are no character columns in the df. Otherwise mgcv will throw an error.
lmm_df <- lmm_df %>% 
  mutate(across(where(is.character), as.factor))

# We are fitting a generalized additive model with approx the same random structure like our LMM, except we are now adding smoothing splines, accounting for the possibility that continuous predictors might have a non-linear relationship with our outcome variable
#--- improving model by increasing k
m_gam_RT_ts2 <- bam(log(duration) ~ 
                cognitive_load +
                s(surprisal_2) + 
                s(age, k = 20) + 
                s(previous_reading_times_log, k = 50) +
                s(dprime, k = 30) +
                s(mean_dprime_singletasks, k = 50) +
                s(compr_Qs_percent_correct_mean, k = 20) +
                s(compr_Qs_percent_correct_diff, k = 10) +
                # lab vs. online:
                recording_location +
                # properties of words:
                s(word_frequency) +
                s(word_length_single) +
                # was there an n-back response in the trial?
                reaction +
                # position of trial in experiment for
                # controlling training & tiredness effects:
                block_nr + trial_nr +
                # entropy
                s(entropy_2) +
                ti(surprisal_2, age, by = cognitive_load) +
                s(surprisal_2, cognitive_load, bs="fs", m=1) +
                s(ID, cognitive_load, bs = "re") +
                s(text_nr, bs = "re") + 
                s(word, bs = "re") + 
                s(colour, bs = "re"),
                data = lmm_df, method="fREML",
              discrete = TRUE, n_threads = 8)

saveRDS(m_gam_RT_ts2, 
        file = "Analysis/RData/Mixed_models/m_gam_RT_ts2.rds")

# check if some predictors need more basis functions, looks good with the current settings
gam.check(m_gam_RT_ts2)

# model output including 
summary(m_gam_RT_ts2)

# draw individual smoothing splines of predictors to get an idea what they look like
draw(m_gam_RT_ts2)

# compare gam model to our lmm: gam actually performs better, accounting for non-linearity of most predictors
model_comp_lmm_gam <- compare_performance(m_gam_RT_ts2, m_RT_ts2_age_centered_random_slope_entropy.rds, rank = T)
saveRDS(model_comp_lmm_gam, 
        file = "Analysis/RData/Mixed_models/model_comp_lmm_gam.rds")


pred <- predict_response(m_gam_RT_ts2, terms = c("age", "surprisal_2", "cognitive_load"))
plot(pred)

slopes <- estimate_slopes(m_gam_RT_ts2, trend = "surprisal_2",
                          by = c("age", "cognitive_load"))
saveRDS(slopes, file = here::here("Analysis/RData/Mixed_models/slopes_gam_ts2.rds"))

plot(slopes) + 
  facet_wrap(~ cognitive_load) + 
  theme_minimal(12) +
  theme(title = element_blank()) + 
  scale_fill_brewer(palette = "Dark2") +
  scale_color_brewer(palette = "Dark2")

# plot output table of model
tab_model(m_gam_RT_ts2, 
          seed = 42,
          show.se = TRUE, 
          show.stat = TRUE,
          show.intercept = FALSE, 
          show.df = TRUE,
          show.re.var = FALSE,
          show.icc = TRUE,
          show.obs = FALSE,
          p.val = 'satterthwaite', 
          p.threshold = c(0.05), # star after all p-values < 0.05
          p.style='scientific',
          digits = 6, 
          digits.p = 3)

```


# Models for Task Performance
--> model dual-task d-primes and comprehension Q performance
``` {r model task performance}
# ---------- dual-task d-primes ----------

# The distribution of the d-primes isn't ideal but we can't use a 
# log or Gamma distribution due to negative d-primes. 
# --> stick to the "normal" distribution for now and use LMM!

# only look at 1-back and 2-back, because there was no n-back task in the BL condition.
lmm_df_dprimes <- subset(lmm_df, cognitive_load != "BL")
lmm_df_dprimes$cognitive_load <- droplevels(lmm_df_dprimes$cognitive_load)

# Assign simple coding scheme for the 2 cognitive load levels:
lmm_df_dprimes$cognitive_load <- as.factor(lmm_df_dprimes$cognitive_load)
c <- contr.treatment(2) # create dummy coding scheme
my.coding <- matrix(rep(1/2, 2), ncol = 1) # make matrix 
my.simple <- c-my.coding
contrasts(lmm_df_dprimes$cognitive_load) <- my.simple

# run model with age = centered:
m_dprimes_age_centered <- lmer(dprime ~ # control diff. response strategies 
                           # on block- and participant-level:
                           mean_dprime_singletasks_centered +
                           compr_Qs_percent_correct_mean_centered +
                           compr_Qs_percent_correct_diff_centered + 
                           # lab vs. online:
                           recording_location + 
                           # position of block in experiment for 
                           # controlling training & tiredness effects:
                           block_nr +
                           age_centered * cognitive_load + 
                           # subject-specific random slope of cognitive load:
                           # cognitive load could have different 
                           # effects on different participants
                           (1 + cognitive_load | ID) + 
                           # random slope for text,
                           # because we picked them "randomly" from a 
                           # billion of possible other texts:
                           (1 | text_nr),
                           data = lmm_df_dprimes,
                           # should restricted maximum likelihood estimation (REML) be used?
                           REML = TRUE, 
                           # choose bobyqa optimizer:
                           lmerControl(optimizer = "bobyqa"))

# run it with uncentered age: 
m_dprimes_no_centering <- lmer(dprime ~ # control diff. response strategies 
                           # on block- and participant-level:
                           mean_dprime_singletasks_centered +
                           compr_Qs_percent_correct_mean_centered +
                           compr_Qs_percent_correct_diff_centered + 
                           # lab vs. online:
                           recording_location + 
                           # position of block in experiment for 
                           # controlling training & tiredness effects:
                           block_nr +
                           age * cognitive_load + 
                           # subject-specific random slope of cognitive load:
                           # cognitive load could have different 
                           # effects on different participants
                           (1 + cognitive_load | ID) + 
                           # random slope for text,
                           # because we picked them "randomly" from a 
                           # billion of possible other texts:
                           (1 | text_nr),
                           data = lmm_df_dprimes,
                           # should restricted maximum likelihood estimation (REML) be used?
                           REML = TRUE, 
                           # choose bobyqa optimizer:
                           lmerControl(optimizer = "bobyqa"))

# save model outputs:
saveRDS(m_dprimes_age_centered, 
        file = here::here("Analysis/RData/m_dprimes_age_centered.rds"))
saveRDS(m_dprimes_no_centering, 
        file = here::here("Analysis/RData/m_dprimes_no_age_centering.rds"))


# print results: 
message("Results for d-primes:")

# table with FDR-corrected p-values:
tab_model(m_dprimes_no_centering, 
          seed = 42,
          show.se = TRUE, 
          show.stat = FALSE,
          show.intercept = FALSE, 
          show.df = FALSE,
          show.re.var = FALSE,
          show.icc = TRUE,
          show.obs = FALSE,
          p.style = "scientific",
          p.threshold = c(0.05), # make star after all values < 0.05
          p.adjust='fdr', 
          df.method = "satterthwaite",
          digits = 6, 
          digits.p = 3)


# get LMM results with p-values
#summary_output <- Anova(m_dprimes)
# get p-values
#p_values <- summary_output$`Pr(>Chisq)`
#print(round(p_values, digits = 3))
# run FDR correction
#p_values_fdr <- round(p.adjust(p_values, method = "fdr"), digits = 3)
# update p-values in the table
#summary_output$`Pr(>Chisq)` <- p_values_fdr
#print(summary_output)
#print(summary(m_dprimes))

# print model fit:
get_gof(m_dprimes_no_centering)


# plot effect of load and age on n-back performance:
marginal_effects_dprime_age_load <- plot(ggeffect(m_dprimes, terms = c("age_centered", "cognitive_load")),
                                               color = palet_load[c(2,3)], # why is only first colour used here?! 
                                               show_ci = T,
                                               line_size = 2, 
                                               alpha = 0.4) + 
                                          coord_cartesian(ylim = c(0, 4.5)) + 
                                          labs(x = "Age", y = "d-prime") +
                                          theme_minimal() + 
                                          theme(panel.grid.minor = element_blank(), 
                                          panel.grid.major = element_blank(),
                                          axis.ticks = element_line(color = "black"),
                                          axis.line = element_line(color = "black")) +
                                          # back-transform centered age variable 
                                          # so it makes more sense here:   
                                          scale_x_continuous(breaks = c(20 - mean_age, 
                                                                        40 - mean_age,
                                                                        60 - mean_age,
                                                                        80 - mean_age), 
                                                             labels = c(20, 40, 60, 80))

ggsave(plot = marginal_effects_dprime_age_load, 
       filename = here::here(paste0("Plots/marginal_effects_dprimes_age_load_", today, ".pdf")),         
       width = 5, height = 6, device = "pdf")


# ---------- comprehension Qs ----------

# edit df_comprehension_Qs a bit. We exclude all training 
# blocks and then reshape it to long format, with all questions 
# in 1 column and the accuracies in another one:
df_comprehension_Qs_long <- df_comprehension_Qs %>% 
                              dplyr::select(-nr_correct) %>% 
                                filter(block_kind != "reading_baseline_training") %>% 
                                    pivot_longer(1:3, 
                                                 names_to = "question", 
                                                 values_to = "accuracy")


# assign simple coding scheme for the 
# variables "block_kind" (aka cognitive load) and "recording_location":
df_comprehension_Qs_long$block_kind <- factor(df_comprehension_Qs_long$block_kind, 
                                              levels = c("Reading_BL_main", "1back_main", "2back_main"))
c <- contr.treatment(3) # create dummy coding scheme
my.coding <- matrix(rep(1/3, 6), ncol = 2) # make matrix 
my.simple <- c-my.coding
contrasts(df_comprehension_Qs_long$block_kind) <- my.simple

df_comprehension_Qs_long$recording_location <- as.factor(df_comprehension_Qs_long$recording_location)
c <- contr.treatment(2) # create dummy coding scheme
my.coding <- matrix(rep(1/2, 2), ncol = 1) # make matrix 
my.simple <- c-my.coding
contrasts(df_comprehension_Qs_long$recording_location) <- my.simple

# center age variable:
df_comprehension_Qs_long$age_cent <- scale(df_comprehension_Qs_long$age, scale = F)

# model comprehension question performance as binomial variable
m_compr_Qs_age_centered <- glmer(accuracy ~ block_kind * age_cent + 
                               recording_location + 
                               (1 | ID) + 
                               (1 | text_nr), 
                               data = df_comprehension_Qs_long, 
                               family = binomial(link = "logit"),
                               glmerControl(optimizer = "bobyqa"))

# run again, but don't center age here:
m_compr_Qs_no_centering <- glmer(accuracy ~ block_kind * age + 
                               recording_location + 
                               (1 | ID) + 
                               (1 | text_nr), 
                               data = df_comprehension_Qs_long, 
                               family = binomial(link = "logit"),
                               glmerControl(optimizer = "bobyqa"))


# Explanation for future Merle: 
# We can't add task performance measures to this model because we don't 
# have any d-primes for the BL condition, so this would mean the 
# block gets kicked out in the model. And adding block_nr does more 
# harm than good because the model fit is lower with block_nr included for some reason.


# save model output:
saveRDS(m_compr_Qs_age_centered, 
        file = here::here("Analysis/RData/m_compr_Qs_age_centered.rds"))

saveRDS(m_compr_Qs_no_centering, 
        file = here::here("Analysis/RData/m_compr_Qs_no_centering.rds"))



# Print the results:
message("Results for comprehension question accuracy:")

# table with FDR-corrected p-values:
tab_model(m_compr_Qs_no_centering, 
          seed = 42,
          show.se = TRUE, 
          show.stat = FALSE,
          show.intercept = FALSE, 
          show.df = FALSE,
          show.re.var = FALSE,
          show.icc = TRUE,
          show.obs = FALSE,
          p.style = "scientific",
          p.threshold = c(0.05), # make star after all values < 0.05
          p.adjust='fdr', 
          df.method = "wald", # use wald here: Kenward-Rogers and Satterthwaite cannot be used for GLMMs
          digits = 6, 
          digits.p = 3)

# get LMM results with p-values
#summary_output <- Anova(m_compr_Qs)
# get p-values
#p_values <- summary_output$`Pr(>Chisq)`
#print(round(p_values, digits = 3))
# run FDR correction
#p_values_fdr <- round(p.adjust(p_values, method = "fdr"), digits = 3)
# update p-values in the table
#summary_output$`Pr(>Chisq)` <- p_values_fdr
#print(summary_output)
#print(summary(m_compr_Qs))

# print model fit:
get_gof(m_compr_Qs_no_centering)




### Plots:

# plot the effects of cognitive load and age:
marginal_effects_comprehension_Qs_age_load <- plot(ggeffect(m_compr_Qs, terms = c("age_cent", "block_kind")),
                                               color = palet_load, # why is only the first colour used here?! 
                                               show_ci = T,
                                               line_size = 2, 
                                               alpha = 0.4) + 
                                                coord_cartesian(ylim = c(0, 1)) + 
                                                labs(x = "Age", y = "% correct answers") +
                                                theme_minimal() + 
                                                theme(panel.grid.minor = element_blank(), 
                                                panel.grid.major = element_blank(),
                                                legend.position = "none",
                                                axis.ticks = element_line(color = "black"),
                                                axis.line = element_line(color = "black")) +
                                                # back-transform centered age variable 
                                                # so it makes more sense here:   
                                                scale_x_continuous(breaks = c(20 - mean_age, 
                                                                              40 - mean_age,
                                                                              60 - mean_age,
                                                                              80 - mean_age), 
                                                                   labels = c(20, 40, 60, 80))

ggsave(plot = marginal_effects_comprehension_Qs_age_load, 
       filename = here::here(paste0("Plots/marginal_effects_comprehension_Qs_age_load_", today, ".pdf")),         
       width = 5, height = 6, device = "pdf")


```

# OLD but maybe usable?
## Exploring GAMs for EXNAT_1
```{r Rev 1}
#---- Comments addressed:
# The potential non-linear relationship between age and performance should be discussed, particularly how older adults might be more affected by increased task load.
# --> add age-squared in our models to account for this non-linearity
#---- Time Scale 1 ----
# linear model with RT transformation
# 
# library(mgcv)
# library(gratia)
# library(itsadug)
# 
# # plot relationship of age and surprisal with RT to see whether using a GAM is "justified"
# x <- lmm_df %>% 
#   group_by(ID, block_names_numbered) %>% 
#   summarise(mean_RT = mean(log(duration)), age = mean(age))
#   
# ggplot(x, aes(x = age, y = mean_RT, group = block_names_numbered)) +
#   #geom_line(linewidth = 0.4) +
#   geom_smooth(method = "loess")
# 
# df <- lmm_df %>% 
#   filter(age>=50)
# 
# lmm_df <- lmm_df %>% 
#   mutate(across(where(is.character), as.factor))
# 
# m_gam1 <- bam(log(duration) ~ 
#                 cognitive_load +
#                 s(surprisal_1_centered) + 
#                 s(age_centered) + 
#                 s(previous_reading_times_log_centered) +
#                 dprime_centered +
#                 mean_dprime_singletasks_centered +
#                 compr_Qs_percent_correct_mean_centered +
#                 compr_Qs_percent_correct_diff_centered +
#                 # lab vs. online:
#                 recording_location +
#                 # properties of words:
#                 s(word_frequency_centered) +
#                 s(word_length_single_centered) +
#                 # was there an n-back response in the trial?
#                 reaction +
#                 # position of trial in experiment for
#                 # controlling training & tiredness effects:
#                 block_nr + trial_nr +
#                 ti(surprisal_1_centered, age_centered, by = cognitive_load) +
#                 s(surprisal_1_centered, ID, bs="fs", m=1) +
#                 s(ID, cognitive_load, bs = "re") +
#                 s(text_nr, bs = "re") + 
#                 s(word, bs = "re") + 
#                 s(colour, bs = "re"),
#                 data = lmm_df, method="fREML",
#               discrete = TRUE)
# save(m_gam1, file = here::here(paste0("Analysis/RData/m_gam1_", today, ".RData")))                
# summary(m_gam1)
# 
# m_gam2 <- bam(log(duration) ~ 
#                 cognitive_load +
#                 s(surprisal_1_centered) + 
#                 s(age_centered) + 
#                 s(previous_reading_times_log_centered) +
#                 dprime_centered +
#                 mean_dprime_singletasks_centered +
#                 compr_Qs_percent_correct_mean_centered +
#                 compr_Qs_percent_correct_diff_centered +
#                 # lab vs. online:
#                 recording_location +
#                 # properties of words:
#                 s(word_frequency_centered) +
#                 s(word_length_single_centered) +
#                 # was there an n-back response in the trial?
#                 reaction +
#                 # position of trial in experiment for
#                 # controlling training & tiredness effects:
#                 block_nr + trial_nr +
#                 ti(surprisal_1_centered, age_centered, by = cognitive_load) +
#                 # s(surprisal_1_centered, ID, bs="fs", m=1) +
#                 s(ID, cognitive_load, bs = "re") +
#                 s(text_nr, bs = "re") + 
#                 s(word, bs = "re") + 
#                 s(colour, bs = "re"),
#                 data = lmm_df, method="fREML",
#               discrete = TRUE)
# save(m_gam2, file = here::here(paste0("Analysis/RData/m_gam2_", today, ".RData")))
# 
# anova(m_gam1, m_gam2, test = "Chisq") # m_gam1 performs better
# 
# appraise(m_gam1)
# draw(m_gam1, select = "ti(surprisal_1_centered, age_centered, by = cognitive_load)")
# 
# m_gam1_NOcentering <- bam(log(duration) ~ 
#                 cognitive_load +
#                 s(surprisal_1) + 
#                 s(age) + 
#                 s(previous_reading_times_log) +
#                 dprime_centered +
#                 mean_dprime_singletasks_centered +
#                 compr_Qs_percent_correct_mean_centered +
#                 compr_Qs_percent_correct_diff_centered +
#                 # lab vs. online:
#                 recording_location +
#                 # properties of words:
#                 s(word_frequency) +
#                 s(word_length_single) +
#                 # was there an n-back response in the trial?
#                 reaction +
#                 # position of trial in experiment for
#                 # controlling training & tiredness effects:
#                 block_nr + trial_nr +
#                 ti(surprisal_1, age, by = cognitive_load) +
#                 s(surprisal_1, ID, bs="fs", m=1) +
#                 s(ID, cognitive_load, bs = "re") +
#                 s(text_nr, bs = "re") + 
#                 s(word, bs = "re") + 
#                 s(colour, bs = "re"),
#                 data = lmm_df, method="fREML",
#               discrete = TRUE)
# save(m_gam1_NOcentering, file = here::here(paste0("Analysis/RData/m_gam1_NoCentering_", today, ".RData")))                
# summary(m_gam1_NOcentering)
# 
# appraise(m_gam1_NOcentering)
# draw(m_gam1_NOcentering)
# 
# m_gam1_allSmooths <- bam(log(duration) ~ 
#                 cognitive_load +
#                 s(surprisal_1) + 
#                 s(age) + 
#                 s(previous_reading_times_log) +
#                 s(dprime) +
#                 s(mean_dprime_singletasks) +
#                 s(compr_Qs_percent_correct_mean) +
#                 s(compr_Qs_percent_correct_diff) +
#                 # lab vs. online:
#                 recording_location +
#                 # properties of words:
#                 s(word_frequency) +
#                 s(word_length_single) +
#                 # was there an n-back response in the trial?
#                 reaction +
#                 # position of trial in experiment for
#                 # controlling training & tiredness effects:
#                 block_nr + trial_nr +
#                 ti(surprisal_1, age, by = cognitive_load) +
#                 s(surprisal_1, cognitive_load, bs="fs", m=1) +
#                 s(ID, cognitive_load, bs = "re") +
#                 s(text_nr, bs = "re") + 
#                 s(word, bs = "re") + 
#                 s(colour, bs = "re"),
#                 data = lmm_df, method="fREML",
#               discrete = TRUE, n_threads = 8)
# 
# appraise(m_gam1_allSmooths)
# draw(m_gam1_allSmooths)
# summary(m_gam1_allSmooths)
# m_gam1_allSmooths_ac <- acf_resid(m_gam1_allSmooths)
# 
# save(m_gam1_allSmooths, file = here::here(paste0("Analysis/RData/m_gam1_allSmooths_", today, ".RData")))
# 
# model_comp <- anova(m_gam1_NOcentering, m_gam1_allSmooths, test = "Chisq")
# 
# tab_model(m_gam1_allSmooths)
# 
# pred <- predict_response(m_gam1_allSmooths, terms = c("age", "cognitive_load"))
# plot(pred)
# 
# slopes <- estimate_slopes(m_gam1_allSmooths, trend = "surprisal_1",
#                           by = c("age", "cognitive_load"))
# save(slopes, file = here::here(paste0("Analysis/RData/slopes_gam_ts1_", today, ".RData")))
# 
# plot(slopes) + 
#   facet_wrap(~ cognitive_load) + 
#   theme_minimal(12) +
#   theme(title = element_blank()) + 
#   scale_fill_brewer(palette = "Dark2") +
#   scale_color_brewer(palette = "Dark2")
# 
# # this basically does the same thing but you get 
# # a cool table with FDR-corrected p-values:
# tab_model(m_RT_ts1_age_centered_random_slope, 
#           show.se = TRUE, 
#           show.stat = TRUE,
#           show.df = TRUE,
#           p.val = 'satterthwaite', 
#           p.adjust='fdr', 
#           #p.style='scientific',
#           digits = 3, 
#           digits.p = 3)
# 
# #--- improving model by increasing k
# m_gam1_MoreSplines <- bam(log(duration) ~ 
#                 cognitive_load +
#                 s(surprisal_1) + 
#                 s(age, k = 50) + 
#                 s(previous_reading_times_log, k = 50) +
#                 s(dprime) +
#                 s(mean_dprime_singletasks, k = 50) +
#                 s(compr_Qs_percent_correct_mean, k = 20) +
#                 s(compr_Qs_percent_correct_diff, k = 20) +
#                 # lab vs. online:
#                 recording_location +
#                 # properties of words:
#                 s(word_frequency) +
#                 s(word_length_single) +
#                 # was there an n-back response in the trial?
#                 reaction +
#                 # position of trial in experiment for
#                 # controlling training & tiredness effects:
#                 block_nr + trial_nr +
#                 ti(surprisal_1, age, by = cognitive_load) +
#                 s(surprisal_1, cognitive_load, bs="fs", m=1) +
#                 s(ID, cognitive_load, bs = "re") +
#                 s(text_nr, bs = "re") + 
#                 s(word, bs = "re") + 
#                 s(colour, bs = "re"),
#                 data = lmm_df, method="fREML",
#               discrete = TRUE, n_threads = 8)
# 
# gam.check(m_gam1_MoreSplines)
# 
# m_gam1_test <- bam(duration ~ 
#                 cognitive_load +
#                 s(surprisal_1) + 
#                 s(age, k = 50) + 
#                 s(previous_reading_times_log, k = 20) +
#                 s(dprime, k = 20) +
#                 s(mean_dprime_singletasks, k = 12) +
#                 s(compr_Qs_percent_correct_mean, k = 12) +
#                 s(compr_Qs_percent_correct_diff, k = 12) +
#                 # lab vs. online:
#                 recording_location +
#                 # properties of words:
#                 s(word_frequency) +
#                 s(word_length_single) +
#                 # was there an n-back response in the trial?
#                 reaction +
#                 # position of trial in experiment for
#                 # controlling training & tiredness effects:
#                 block_nr + trial_nr +
#                 ti(surprisal_1, age, by = cognitive_load) +
#                 s(surprisal_1, cognitive_load, bs="fs", m=1) +
#                 s(ID, cognitive_load, bs = "re") +
#                 s(text_nr, bs = "re") + 
#                 s(word, bs = "re") + 
#                 s(colour, bs = "re"),
#                 data = lmm_df, method="fREML",
#               discrete = TRUE, n_threads = 8,
#               family=scat(link="identity"))
```


# Show Results: Tables and Plots for the LMM Results
## Results Tables
```{r show create tables with LMM results}

# Prepare to wait, this takes a while to run.

# There's a difference between p-values between Anova() and tab_model() depending on how you set "type" in Anova():
# type = "III" tests for the main effect after other main effects and 
# significant (!) interactions. This means p-values for main effects are corrected 
# for the significant interaction(s) and can't really be interpreted anymore. 
# If interactions are not significant though, type II gives a more powerful test. 
# tab_model produces the same p-values as Anova type III.
# Check this: https://md.psych.bio.uni-goettingen.de/mv/unit/lm_cat/lm_cat_unbal_ss_explained.html
#Anova(m_RT_ts2_age_centered_random_slope_entropy, type = "III")

tab_model(m_RT_ts2_age_centered_random_slope_entropy, 
          seed = 42,
          show.se = TRUE, 
          show.stat = TRUE,
          show.intercept = FALSE, 
          show.df = FALSE,
          show.re.var = FALSE,
          show.icc = TRUE,
          show.obs = FALSE,
          p.style = "scientific",
          p.threshold = c(0.05), # star after all p-values < 0.05
          p.adjust = "fdr", # NULL
          df.method = "satterthwaite",
          digits = 6, 
          digits.p = 3)
# Hint: If this throws an error, try updating packages 
#       "purr", "sjPlot" and "parameters", and turn R off and on again. 


# get LMM results with p-values
#summary_output <- Anova(m_RT_ts2_age_centered_random_slope_entropy, 
#                        test.statistic = "Chisq") # use Wald approximation to compute p-values
# get p-values
#p_values <- summary_output$`Pr(>Chisq)`
#print(round(p_values, digits = 10))
# run FDR correction
#p_values_fdr <- round(p.adjust(p_values, method = "fdr"), digits = 10)
# update p-values in the table
#summary_output$`Pr(>Chisq)` <- p_values_fdr
#print(summary_output)
#print(summary(m_RT_ts2_age_centered_random_slope_entropy))

# Print model fits:
message("model fit for LMM:")
get_gof(m_RT_ts2_age_centered_random_slope_entropy)


```    


## Plot marginal effects (main effects, 2-way interactions & 3-way interactions)
```{r plot effects, echo = TRUE}
# plot random effects:
#install.packages("glmmTMB", type="source")
#library(glmmTMB)
#sjPlot::plot_model(mixed.lmer4_prev, type = "re")
# This doesn't work for some reason

# plot estimates for models (or you just print the summary)
sjPlot::plot_model(m_compr_Qs)


#### PLOT 3-WAY INTERACTION OF AGE, SURPRISAL AND LOAD (FOR ALL TIME SCALES)################

# ages are: 27, 45, 62
marginal_effects_3way_interaction <- plot(predict_response(m_RT_ts2_age_centered_random_slope_entropy,  
                                    terms = c("surprisal_2_centered",  
                                              "cognitive_load",  
                                              "age_centered")),  
                                    line_size = 2,   
                                    colors = palet_load) +  
                                    theme_sjplot2() +  
                                    theme(axis.line.x = element_line(color = "black")) +  
                                    scale_x_continuous(breaks = c(0 - mean(lmm_df$surprisal_2),  
                                                                    20 - mean(lmm_df$surprisal_2),  
                                                                    40 - mean(lmm_df$surprisal_2),  
                                                                    60 - mean(lmm_df$surprisal_2),  
                                                                    80 - mean(lmm_df$surprisal_2)),  
                                                        labels = c(0, 20, 40, 60, 80)) +  
                                    scale_y_continuous(breaks = c(400, 600, 800, 1000, 1200, 1400, 1600)) +
                                    theme_minimal() +  
                                    theme(panel.grid.minor = element_blank(),  
                                          panel.grid.major = element_blank(),  
                                          axis.ticks = element_line(color = "black"),  
                                          axis.line = element_line(color = "black"))  

ggsave(plot = marginal_effects_3way_interaction, 
       filename = here::here(paste0("Plots/marginal_effects_3way_interaction_", today, ".pdf")),  
       width = 7, height = 5, device = "pdf")


#####PLOT 2-WAY INTERACTION OF COGNITIVE LOAD & SURPRISAL ###############
mean_age <- mean(as.numeric(subset(df_demogr, excl == F)$age))
sd_age   <- sd(as.numeric(subset(df_demogr, excl == F)$age))
mean_surprisal <- mean(lmm_df$surprisal_2)

# How old are M-1SD, M, M+1SD?
mean_age+sd_age
mean_age
mean_age-sd_age

plot_int_surprisal_load <- plot(predict_response(m_RT_ts2_age_centered_random_slope_entropy,
                                                 terms = c("surprisal_2_centered", "cognitive_load")), 
                                     line_size = 2,
                                     alpha = 0.4, 
                                     colors = palet_load) +
                            labs(x = "Surprisal", y = "Reading Time in ms") +
                            theme_minimal() + 
                            theme(panel.grid.minor = element_blank(), 
                                  panel.grid.major = element_blank(),
                                  axis.ticks = element_line(color = "black"),
                                  axis.line = element_line(color = "black")) + 
                            coord_cartesian(ylim = c(200, 2000)) +
                            scale_y_continuous(breaks = c(200, 400, 600, 
                                                          800, 1000, 
                                                          1200, 1400, 1600, 1800, 2000)) +
                            scale_x_continuous(breaks = c(0 - mean_surprisal, 
                                                          20 - mean_surprisal, 
                                                          40 - mean_surprisal,
                                                          60 - mean_surprisal,
                                                          80 - mean_surprisal), 
                                               labels = c(0, 20, 40, 60, 80))

ggsave(plot = plot_int_surprisal_load, 
       filename = here::here(paste0("Plots/marginal_effects_surprisal_load_", today, ".pdf")),  
       width = 7, height = 5, device = "pdf")


plot_int_age_load <- plot(predict_response(m_RT_ts2_age_centered_random_slope_entropy,
                                                 terms = c("age_centered", "cognitive_load")), 
                                     line_size = 2,
                                     alpha = 0.4, 
                                     colors = palet_load) +
                            labs(x = "Age", y = "Reading Time in ms") +
                            theme_minimal() + 
                            theme(panel.grid.minor = element_blank(), 
                                  panel.grid.major = element_blank(),
                                  axis.ticks = element_line(color = "black"),
                                  axis.line = element_line(color = "black")) + 
                            coord_cartesian(ylim = c(200, 2000)) +
                            scale_y_continuous(breaks = c(200, 400, 600, 
                                                          800, 1000, 
                                                          1200, 1400, 1600, 1800, 2000))+
                              scale_x_continuous(breaks = c(20 - mean_age, 
                                                            40 - mean_age,
                                                            60 - mean_age,
                                                            80 - mean_age), 
                                                             labels = c(20, 40, 60, 80))

ggsave(plot = plot_int_age_load, 
       filename = here::here(paste0("Plots/marginal_effects_age_load_", today, ".pdf")),  
       width = 7, height = 5, device = "pdf")


plot_int_age_surprisal <- plot(predict_response(m_RT_ts2_age_centered_random_slope_entropy,
                                                 terms = c("surprisal_2_centered", "age_centered")), 
                                     line_size = 2,
                                     alpha = 0.4, 
                                     colors = c("#69a3c2", "#4c768c","#365464")) + 
                            labs(x = "Surprisal", y = "Reading Time in ms") +
                            theme_minimal() + 
                            theme(panel.grid.minor = element_blank(), 
                                  panel.grid.major = element_blank(),
                                  axis.ticks = element_line(color = "black"),
                                  axis.line = element_line(color = "black")) + 
                            coord_cartesian(ylim = c(200, 2000)) +
                            scale_y_continuous(breaks = c(200, 400, 600, 
                                                          800, 1000, 
                                                          1200, 1400, 1600, 1800, 2000)) +
                                scale_x_continuous(breaks = c(0 - mean_surprisal,
                                                              20 - mean_surprisal, 
                                                              40 - mean_surprisal,
                                                              60 - mean_surprisal,
                                                              80 - mean_surprisal), 
                                                             labels = c(0, 20, 40, 60, 80))
ggsave(plot = plot_int_age_surprisal, 
       filename = here::here(paste0("Plots/marginal_effects_age_surprisal_", today, ".pdf")),  
       width = 7, height = 5, device = "pdf")
                                          
                                          

##### PLOT MAIN EFFECTS ###############

# Age, Surprisal and Load 

# Reading gets a lot slower with increasing age:
plot_age <- plot(predict_response(m_RT_ts2_age_centered_random_slope_entropy,
                                     terms = c("age_centered")), 
                                     line.size = 2,
                                     alpha = 0.4, 
                                     colors = palet_effects) + 
                            labs(x = "Age", y = "Reading Time (in ms)") +
                            theme_minimal() + 
                            theme(panel.grid.minor = element_blank(), 
                                  panel.grid.major = element_blank(),
                                  axis.ticks = element_line(color = "black"),
                                  axis.line = element_line(color = "black")) + 
                            scale_x_continuous(breaks = c(20, 40, 60, 80), 
                                               labels = c(20, 40, 60, 80)) +
                            coord_cartesian(ylim = c(200, 1400)) +
                            scale_y_continuous(breaks = c(200, 400, 600, 
                                                          800, 1000, 
                                                          1200, 1400)) +
                            scale_x_continuous(breaks = c(20 - mean_age, 
                                                          40 - mean_age,
                                                          60 - mean_age,
                                                          80 - mean_age), 
                                               labels = c(20, 40, 60, 80))

# Calculate how much reading slows down with a 1 year increase in age:
exp(0.009113264) # put beta for age effect here: Gives you the change in % for a change of 1 year in age

# Now check our mean RT, divide by 100 and multiply by exp(0.009113264) to get change in RT
mean(lmm_df$duration)/100 * exp(0.009113264) 




# Reading gets a lot slower with increasing load:
plot_load <- plot(predict_response(m_RT_ts2_age_centered_random_slope_entropy,
                                     terms = c("cognitive_load")), 
                                     line.size = 2,
                                     alpha = 0.4, 
                                     colors = palet_load) + 
                            labs(x = "Cognitive Load", y = "Reading Time (in ms)") +
                            theme_minimal() + 
                            theme(panel.grid.minor = element_blank(), 
                                  panel.grid.major = element_blank(),
                                  axis.ticks = element_line(color = "black"),
                                  axis.line = element_line(color = "black")) + 
                            coord_cartesian(ylim = c(200, 1400)) +
                            scale_y_continuous(breaks = c(200, 400, 600, 
                                                          800, 1000, 
                                                          1200, 1400))

# Reading gets slower with increasing surprisal:
plot_surprisal <- plot(predict_response(m_RT_ts2_age_centered_random_slope_entropy,
                                     terms = c("surprisal_2_centered")), 
                                     line.size = 2,
                                     alpha = 0.4, 
                                     colors = palet_effects) + 
                            labs(x = "Surprisal", y = "Reading Time (in ms)") +
                            theme_minimal() + 
                            theme(panel.grid.minor = element_blank(), 
                                  panel.grid.major = element_blank(),
                                  axis.ticks = element_line(color = "black"),
                                  axis.line = element_line(color = "black")) + 
                            coord_cartesian(ylim = c(200, 1400)) +
                            scale_y_continuous(breaks = c(200, 400, 600, 
                                                          800, 1000, 
                                                          1200, 1400)) +
                            scale_x_continuous(breaks = c(0 - mean_surprisal,
                                                          20 - mean_surprisal, 
                                                          40 - mean_surprisal,
                                                          60 - mean_surprisal,
                                                          80 - mean_surprisal), 
                                               labels = c(0, 20, 40, 60, 80))


# Combine the 3 plots so each is 1 column:
marginal_effects_age_surprisal_load <- grid.arrange(plot_age, 
                                         plot_load, 
                                         plot_surprisal,
                                         widths = c(1.2, 1, 1),
                                         nrow = 1)
ggsave(plot = marginal_effects_age_surprisal_load, 
       filename = here::here(paste0("Plots/marginal_effects_age_surprisal_load_", today, ".pdf")),  
       width = 10, height = 5, device = "pdf")





## OLD: 

#main_eff <- effect("surprisal_2_centered", m_RT_ts2_No_centering_age_random_slope_entropy)

# Estimate marginal means for some effects we controlled for:
# --> use the model with uncentered age variable here:
#main_eff_dprime <- effect("dprime_centered", m_RT_ts2_No_centering_age_random_slope_entropy)
#main_eff_comprQs_mean <- effect("compr_Qs_percent_correct_mean_centered", #m_RT_ts2_No_centering_age_random_slope_entropy)
#main_eff_comprQs_diff <- effect("compr_Qs_percent_correct_diff_centered", #m_RT_ts2_No_centering_age_random_slope_entropy)
#main_eff_cognload <- effect("cognitive_load", m_RT_ts2_No_centering_age_random_slope_entropy)


# On block-level, reading gets a lot slower with increasing d-prime.
#plot_main_eff_dprime <- plot(x = main_eff_dprime,
#                              confint = list(style = "auto"), # add CIs
#                              main = "Main Effect 'd-Prime Mean'",
#                              xlab = "d-prime",
#                              ylab = "log reading times",
#                              ylim = c(6, 7.1),
#                              type = "response",
#                              rug = FALSE,
#                              lines = list(col = "#365464", lwd = 7))

# same with performance in the comprehension Qs (on participant level): 
# People who take longer are better in the comprehension Qs. Maybe those are the people who read more carefully in general.
#plot_main_eff_comprQs_mean <- plot(x = main_eff_comprQs_mean,
#                              confint = list(style = "auto"), # add CIs
#                              main = "Main Effect '% Correct in Comprehension Qs Mean'",
#                              xlab = "% correct",
#                              ylab = "log reading times",
#                              ylim = c(6, 7.1),
#                              type = "response",
#                              rug = FALSE,
#                              lines = list(col = "#365464", lwd = 7))

# --> completely different story on block level: High reading speed seems to be linked to high comprehension Q performance. 
# Maybe facilitated comprehension makes people faster.
#plot_main_eff_comprQs_diff <- plot(x = main_eff_comprQs_diff,
#                              confint = list(style = "auto"), # add CIs
#                              main = "Main Effect '% Correct in Comprehension Qs Diff'",
#                              xlab = "% correct",
#                              ylab = "log reading times",
#                              ylim = c(6, 7.1),
#                              type = "response",
#                              rug = FALSE,
#                              lines = list(col = "#365464", lwd = 7))

# Reading gets a lot slower with increasing cognitive load:
#plot_main_eff_cognload <- plot(x = main_eff_cognload,
#                               confint = list(style = "auto"), # add CIs
#                               main = "Main Effect 'Cognitive Load'",
#                               xlab = "Cognitive Load Condition",
#                               ylab = "log reading times",
#                               ylim = c(6, 7.1),
#                               type = "response",
#                               rug = FALSE,
#                               lines = list(col = "#365464", lwd = 7))

# Reading gets a little slower with increasing word surprisal:
#plot_main_eff_surprisal <- plot(x = main_eff,
#                      confint = list(style = "auto"), # add CIs
#                      main = "Main Effect 'Surprisal'",
#                      xlab = "Surprisal",
#                      ylab = "log reading times",
#                      ylim = c(6, 7.1),
#                      type = "response",
#                      rug = FALSE,
#                      lines = list(col = "#365464", lwd = 7))

```


````{r plot simple slopes}

# Load simple slopes results:
#load(here::here("Analysis/RData/simslopes_ts2.RData")) 

## load individual plots into variables & change line & fill colour

baseline <- ss_RT_ts2_noCentering_full_random_structure$jn[[1]]$plot +
                scale_color_manual(values = palet_simple_slopes) +
                scale_fill_manual(values = palet_simple_slopes)
one_back <- ss_RT_ts2_noCentering_full_random_structure$jn[[2]]$plot +
                scale_color_manual(values = palet_simple_slopes[2]) +
                scale_fill_manual(values = palet_simple_slopes[2])
two_back <- ss_RT_ts2_noCentering_full_random_structure$jn[[3]]$plot +
                scale_color_manual(values = palet_simple_slopes[2]) +
                scale_fill_manual(values = palet_simple_slopes[2])


## for each time scale, merge all plots together into one column
simslopes <- ggarrange(baseline + coord_cartesian(ylim = c(-0.001, 0.0075)) +
                           theme(legend.position = "none",
                                 axis.title.x = element_blank(),
                                 axis.ticks.x = element_blank(),
                                 axis.text.x = element_blank(),
                                 axis.title.y = element_blank()) +
                           labs(title = "EXNAT-1: Full Sample"),
                           one_back + coord_cartesian(ylim = c(-0.001, 0.0075)) +
                           theme(legend.position = "none",
                                 axis.title.x = element_blank(),
                                 axis.ticks.x = element_blank(),
                                 axis.text.x = element_blank(),
                                 axis.title.y = element_blank()) +
                           labs(title = NULL),
                           two_back + coord_cartesian(ylim = c(-0.001, 0.0075)) +
                           theme(legend.position = "none",
                                 axis.title.x = element_blank(),
                                 axis.title.y = element_blank()) +
                           scale_x_continuous(breaks = c(20, 40, 60, 80)) +
                           labs(title = NULL), 
                           ncol = 1)

ggsave(plot = simslopes, 
       filename = here::here(paste0("Plots/simple_slopes_", today, ".pdf")),
       width = 3, height = 5, device = "pdf")

````
